---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE,
  message   = TRUE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

# `provider` <img src="man/figures/logo.svg" align="right" height="200" />

<!-- badges: start -->
[![R-CMD-check](https://github.com/andrewallenbruce/provider/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/provider/actions/workflows/R-CMD-check.yaml)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![License: MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://choosealicense.com/licenses/mit/)
[![code size](https://img.shields.io/github/languages/code-size/andrewallenbruce/provider.svg)](https://github.com/andrewallenbruce/provider)
[![last commit](https://img.shields.io/github/last-commit/andrewallenbruce/provider.svg)](https://github.com/andrewallenbruce/provider/commits/main)
[![pkgdown](https://github.com/andrewallenbruce/provider/actions/workflows/pkgdown.yaml/badge.svg)](https://github.com/andrewallenbruce/provider/actions/workflows/pkgdown.yaml)
[![Codecov test coverage](https://codecov.io/gh/andrewallenbruce/provider/branch/main/graph/badge.svg)](https://app.codecov.io/gh/andrewallenbruce/provider?branch=main)
[![CodeFactor](https://www.codefactor.io/repository/github/andrewallenbruce/provider/badge)](https://www.codefactor.io/repository/github/andrewallenbruce/provider)
![GitHub milestone](https://img.shields.io/github/milestones/progress/andrewallenbruce/provider/1?color=white&logo=milestones)
<!-- badges: end -->

> Providing easy access to [healthcare provider](https://en.wikipedia.org/wiki/Health_care_provider) data through publicly available APIs & sources.
 

<br>

## Installation

You can install the development version of `provider` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("andrewallenbruce/provider")
```

## Motivation

<br>

The *overarching* goal of `provider` is to make the experience of accessing publicly-available Provider data easier and more consistent across a variety of CMS sources. It aims to accomplish this through the following *general* goals, where possible:

   * Harmonization of variable names so as to allow for removal of duplicate information across API output, if desired
   * Validation checks of provider identifiers (e.g., NPI, PAC ID, Medicare Enrollment ID, CCN)
   * Structuring output in the *tidy* framework as much as is reasonably possible (with an option to turn off by setting `tidy = FALSE`)

<br>


## APIs

API Search functions can be grouped according to the type of data they return about a provider: *administrative*, *statistical*, and *auxillary.*

### Administrative

   * `nppes_npi()`: Registry of all healthcare providers.
   * `provider_enrollment()`: Providers actively enrolled in Medicare.
   * `opt_out()`: Providers currently opted out of Medicare.
   * `revalidation_*()`: Link Type-1 and Type-2 providers.
   * `doctors_and_clinicians()`: Provider school, graduation year, linking.
   * `facility_affiliations()`: Linking providers to Facilities.
   * `hospital_enrollment()`: Facilities linked to providers.

### Statistical

The following return provider-specific stats:

   * `physician_by_provider()`: Yearly high-level utilization data.
   * `physician_by_service()`: Yearly detailed utilization data.
   * `quality_payments()`: Yearly QPP/MIPS performance data.
   * `quality_eligibility()`: Yearly QPP/MIPS eligibility data.
   * `open_payments()`: Yearly Open Payments reporting data.

The following return yearly stats useful for comparison against data returned from `physician_by_service()`:

   * `physician_by_geography()`
   * `beneficiary_enrollment()`
   * `cc_multiple()`
   * `cc_specific()`

### Auxillary

   * `order_refer()`: Is a provider eligible to order and refer?
   * `missing_information()`: Is a provider missing Endpoints in the NPPES NPI Registry?
   * `pending_applications()`: Has a provider's Medicare application been processed?
   * `taxonomy_crosswalk()`: Is a provider's specialty eligible to enroll in Medicare?

<br>

## Usage

```{r echo=TRUE}
library(provider)
```



------------------------------------------------------------------------------

## Code of Conduct

Please note that the `provider` project is released with a [Contributor Code of Conduct](https://andrewallenbruce.github.io/provider/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

