---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE,
  message   = TRUE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

# provider <img src="man/figures/logo.svg" align="right" height="200" />

<!-- badges: start -->
[![devel version](https://img.shields.io/badge/devel%20version-0.0.0.9012-blue.svg)](https://github.com/andrewallenbruce/provider)
[![R-CMD-check](https://github.com/andrewallenbruce/provider/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/provider/actions/workflows/R-CMD-check.yaml)
[![License: MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://choosealicense.com/licenses/mit/)
[![code size](https://img.shields.io/github/languages/code-size/andrewallenbruce/provider.svg)](https://github.com/andrewallenbruce/provider)
[![last commit](https://img.shields.io/github/last-commit/andrewallenbruce/provider.svg)](https://github.com/andrewallenbruce/provider/commits/main)
[![pkgdown](https://github.com/andrewallenbruce/provider/actions/workflows/pkgdown.yaml/badge.svg)](https://github.com/andrewallenbruce/provider/actions/workflows/pkgdown.yaml)
[![Codecov test coverage](https://codecov.io/gh/andrewallenbruce/provider/branch/main/graph/badge.svg)](https://app.codecov.io/gh/andrewallenbruce/provider?branch=main)
[![CodeFactor](https://www.codefactor.io/repository/github/andrewallenbruce/provider/badge)](https://www.codefactor.io/repository/github/andrewallenbruce/provider)
![GitHub milestone](https://img.shields.io/github/milestones/progress/andrewallenbruce/provider/1?color=white&logo=milestones)
<!-- badges: end -->

> Providing easy access to [healthcare provider](https://en.wikipedia.org/wiki/Health_care_provider) data through publicly available APIs.

## Installation

You can install `provider` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("andrewallenbruce/provider")
```

## Usage

```{r echo=TRUE}
library(provider)
```



   - `nppes()`: Registry of all healthcare providers.
   - `providers()`: Providers actively enrolled in Medicare.
   - `opt_out()`: Providers currently opted out of Medicare.
   - `order_refer()`: Is a provider eligible to order and refer?
   - `reassignments`()`: Link Type-1 and Type-2 providers.
   - `clinicians()`: Provider school, graduation year, linking.
   - `affiliations()`: Linking providers to Facilities.
   - `hospitals()`: Hospitals actively enrolled in Medicare.
   - `utilization()`: Yearly high-level utilization data.
   - `quality_payment()`: Yearly QPP/MIPS performance data.
   - `open_payments()`: Yearly Open Payments reporting data.
   - `beneficiaries()`
   - `conditions()`


```{r}
providers(first = "ANDREW", state = "GA", specialty_code = "14-93")
```




------------------------------------------------------------------------------

## Code of Conduct

Please note that the `provider` project is released with a [Contributor Code of Conduct](https://andrewallenbruce.github.io/provider/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

