---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  warning = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `provider` <img src="man/figures/logo.svg" align="right" height="300" />

<!-- badges: start -->
[![R-CMD-check](https://github.com/andrewallenbruce/provider/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/provider/actions/workflows/R-CMD-check.yaml)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![License: MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://choosealicense.com/licenses/mit/)
[![code size](https://img.shields.io/github/languages/code-size/andrewallenbruce/provider.svg)](https://github.com/andrewallenbruce/provider)
[![last commit](https://img.shields.io/github/last-commit/andrewallenbruce/provider.svg)](https://github.com/andrewallenbruce/provider/commits/main)
<!-- badges: end -->

The goal of {provider} is to provide performant and reliable open-source tools to facilitate easy access to [healthcare provider](https://en.wikipedia.org/wiki/Health_care_provider) data through publicly available APIs & sources.

<br>

## Installation

You can install the development version of `provider` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andrewallenbruce/provider")

# install.packages("remotes")
remotes::install_github("andrewallenbruce/provider")
```
<br>

## Search the NPPES by A Provider's NPI

Enter the 10-digit NPI you wish to search for into `prov_npi_nppes()`:

```{r warning=FALSE}
# Load library
library(provider)

# Query the NPPES API
nppes_npi_response <- prov_npi_nppes(1528060837)
```

<br>

This returns a response in the form of a data frame with the NPI searched for, the date & time that the search was performed, the outcome (*results* means the search was successful, *errors*, that something went wrong) and a column called `data_lists`:

<br>

```{r echo=FALSE}
nppes_npi_response
```

<br>

`data_lists` is a nested list-column. You can access the inner lists using the `$` operator, but we can get a better sense of the hierarchical structure of these list columns using lobstr's `tree()` function:

<br>

```{r}
lobstr::tree(nppes_npi_response$data_lists, 
             max_depth = 2)
```

<br>

This exposes seven more nested list-columns, but using the `prov_nppes_unpack()` function, we can untangle this mess:

<br>

```{r message=FALSE}
# Unpack NPPES response
nppes_npi_unpacked <- prov_nppes_unpack(nppes_npi_response)
```

<br>

And the final tidied results:

<br>

```{r echo=FALSE}
nppes_npi_unpacked |> 
  dplyr::select(!c(
    id, 
    middle_name, 
    sole_proprietor, 
    enumeration_date, 
    last_updated, 
    status, 
    name_prefix, 
    name_suffix,
    #location_address_2,
    #mailing_address_2,
    # mailing_state,
    # mailing_zip,
    # mailing_phone,
    # mailing_fax,
    taxon_primary,
    taxon_state,
    ident_code, 
    ident_state)) |> 
  knitr::kable(align = "l")
  #kableExtra::scroll_box(height = "500px", fixed_thead = TRUE)
```

<br>

## Usage

Read the Overview vignette for a more thorough introduction to the package's functionality.

<br>

## Code of Conduct

Please note that the provider project is released with a [Contributor Code of Conduct](https://andrewallenbruce.github.io/provider/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
