---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = FALSE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 150, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

# `provider` <img src="man/figures/logo.svg" align="right" height="200" />

<!-- badges: start -->
[![R-CMD-check](https://github.com/andrewallenbruce/provider/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/provider/actions/workflows/R-CMD-check.yaml)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![License: MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://choosealicense.com/licenses/mit/)
[![code size](https://img.shields.io/github/languages/code-size/andrewallenbruce/provider.svg)](https://github.com/andrewallenbruce/provider)
[![last commit](https://img.shields.io/github/last-commit/andrewallenbruce/provider.svg)](https://github.com/andrewallenbruce/provider/commits/main)
[![Codecov test coverage](https://codecov.io/gh/andrewallenbruce/provider/branch/main/graph/badge.svg)](https://app.codecov.io/gh/andrewallenbruce/provider?branch=main)
[![CodeFactor](https://www.codefactor.io/repository/github/andrewallenbruce/provider/badge)](https://www.codefactor.io/repository/github/andrewallenbruce/provider)
<!-- badges: end -->

The goal of `provider` is to provide performant and reliable open-source tools to facilitate easy access to [healthcare provider](https://en.wikipedia.org/wiki/Health_care_provider) data through publicly available APIs & sources.
 
<br>

```{r results='asis', echo=FALSE}
nppes_func <- gluedown::md_code("nppes_npi()")
nppes_link <- gluedown::md_link("NPPES National Provider Identifier (NPI) Registry" = "https://npiregistry.cms.hhs.gov/search")

mppe_func  <- gluedown::md_code("provider_enrollment()")
mppe_link  <- gluedown::md_link("Medicare Fee-For-Service Public Provider Enrollment" = "https://data.cms.gov/provider-characteristics/medicare-provider-supplier-enrollment/medicare-fee-for-service-public-provider-enrollment")

mme_func   <- gluedown::md_code("beneficiary_enrollment()")
mme_link   <- gluedown::md_link("Medicare Monthly Enrollment" = "https://data.cms.gov/summary-statistics-on-beneficiary-enrollment/medicare-and-medicaid-reports/medicare-monthly-enrollment")

miss_func  <- gluedown::md_code("missing_information()")
miss_link  <- gluedown::md_link("CMS Public Reporting of Missing Digital Contact Information" = "https://data.cms.gov/provider-compliance/public-reporting-of-missing-digital-contact-information")

order_func <- gluedown::md_code("order_refer()")
order_link <- gluedown::md_link("Medicare Order and Referring" = "https://data.cms.gov/provider-characteristics/medicare-provider-supplier-enrollment/order-and-referring")

opt_func   <- gluedown::md_code("opt_out()")
opt_link   <- gluedown::md_link("Medicare Opt Out Affidavits" = "https://data.cms.gov/provider-characteristics/medicare-provider-supplier-enrollment/opt-out-affidavits")

pbp_link   <- gluedown::md_link("Medicare Physician & Other Practitioners: by Provider" = "https://data.cms.gov/provider-summary-by-type-of-service/medicare-physician-other-practitioners/medicare-physician-other-practitioners-by-provider")
pbp_func   <- gluedown::md_code("physician_by_provider()")

pbs_link   <- gluedown::md_link("Medicare Physician & Other Practitioners: by Provider and Service" = "https://data.cms.gov/provider-summary-by-type-of-service/medicare-physician-other-practitioners/medicare-physician-other-practitioners-by-provider-and-service")
pbs_func   <- gluedown::md_code("physician_by_service()")

pbg_link   <- gluedown::md_link("Medicare Physician & Other Practitioners: by Geography and Service" = "https://data.cms.gov/provider-summary-by-type-of-service/medicare-physician-other-practitioners/medicare-physician-other-practitioners-by-geography-and-service")
pbg_func   <- gluedown::md_code("physician_by_geography()")

redd_func  <- gluedown::md_code("revalidation_date()")
redd_link  <- gluedown::md_link("Medicare Revalidation Due Date" = "https://data.cms.gov/provider-characteristics/medicare-provider-supplier-enrollment/revalidation-due-date-list")

recl_func  <- gluedown::md_code("revalidation_group()")
recl_link  <- gluedown::md_link("Medicare Revalidation Clinic Group Practice Reassignment" = "https://data.cms.gov/provider-characteristics/medicare-provider-supplier-enrollment/revalidation-clinic-group-practice-reassignment")

ccs_func   <- gluedown::md_code("cc_specific()")
ccs_link   <- gluedown::md_link("Medicare Specific Chronic Conditions" = "https://data.cms.gov/medicare-chronic-conditions/specific-chronic-conditions")

ccm_func   <- gluedown::md_code("cc_multiple()")
ccm_link   <- gluedown::md_link("Medicare Multiple Chronic Conditions" = "https://data.cms.gov/medicare-chronic-conditions/multiple-chronic-conditions")

clia_func  <- gluedown::md_code("clia_labs()")
clia_link  <- gluedown::md_link("Medicare Provider of Services File - Clinical Laboratories" = "https://data.cms.gov/provider-characteristics/hospitals-and-other-facilities/provider-of-services-file-clinical-laboratories")

tax_func   <- gluedown::md_code("taxonomy_crosswalk()")
tax_link   <- gluedown::md_link("Medicare Provider and Supplier Taxonomy Crosswalk" = "https://data.cms.gov/provider-characteristics/medicare-provider-supplier-enrollment/medicare-provider-and-supplier-taxonomy-crosswalk")



gluedown::md_table(
          data.frame(
  Function = c(nppes_func, 
               mppe_func, 
               mme_func,
               order_func,
               opt_func,
               pbp_func,
               pbs_func,
               pbg_func,
               redd_func,
               recl_func,
               ccs_func,
               ccm_func,
               clia_func,
               tax_func,
               miss_func
               ), 
  API      = c(nppes_link, 
               mppe_link,
               mme_link,
               order_link,
               opt_link,
               pbp_link,
               pbs_link,
               pbg_link,
               redd_link,
               recl_link,
               ccs_link,
               ccm_link,
               clia_link,
               tax_link,
               miss_link
               )))
```
<br>

## Installation

You can install the development version of `provider` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andrewallenbruce/provider")

# install.packages("remotes")
remotes::install_github("andrewallenbruce/provider")
```
<br>

# NPPES National Provider Identifier (NPI) Registry

<br>

```{r echo=TRUE}
# Load library
library(provider)

ex <- nppes_npi(npi = 1083879860)
```


```{r echo=FALSE}
ex |> 
  tidyr::unnest(cols = c(basic, addresses, taxonomies, endpoints), 
                names_repair = "universal") |> 
  dplyr::select(-identifiers, -other_names, -taxonomy_group, 
                -practice_locations, -useDescription, 
                -contentTypeDescription) |> 
  dplyr::mutate(dplyr::across(everything(), as.character)) |> 
  tidyr::pivot_longer(cols = dplyr::everything(), 
                      names_to = "name", 
                      values_to = "value") |> gluedown::md_table()
```


<br>

# Medicare Fee-For-Service Public Provider Enrollment API

<br>

```{r echo=TRUE}
exa <- provider_mppe(npi = ex$number)
```

```{r echo=FALSE}
exa |> tidyr::pivot_longer(cols = dplyr::everything(), 
                      names_to = "name", 
                      values_to = "value") |> gluedown::md_table()
```

<br>

# Medicare Order and Referring API

```{r results='asis'}
order_refer(ex$number) |> 
  dplyr::mutate(dplyr::across(everything(), as.character)) |> 
  tidyr::pivot_longer(cols = dplyr::everything(), 
                      names_to = "name", 
                      values_to = "value") |> gluedown::md_table()
```

<br>

# Medicare Provider and Supplier Taxonomy Crosswalk API

<br>

```{r results='asis'}
provider_mpstc(ex$taxonomies[[1]]$code) |> 
  dplyr::mutate(dplyr::across(everything(), as.character)) |> 
  tidyr::pivot_longer(cols = dplyr::everything(), 
                      names_to = "name", 
                      values_to = "value") |> gluedown::md_table()
```

<br>

# Medicare Revalidation Due Date API

<br>

```{r results='asis'}
provider_mrdd(ex$number) |> 
  dplyr::mutate(dplyr::across(everything(), as.character)) |> 
  tidyr::pivot_longer(cols = dplyr::everything(), 
                      names_to = "name", 
                      values_to = "value") |> gluedown::md_table()
```

<br>

# CMS Public Reporting of Missing Digital Contact Information API

<br>

```{r results='asis'}
provider_promdci(1144224569) |> gluedown::md_table()
```

<br>

# Medicare Opt-Out Affidavits API

<br>

```{r results='asis'}
opt_out(last = "Aaron") |> 
  dplyr::mutate(dplyr::across(everything(), as.character)) |> 
  tidyr::pivot_longer(cols = dplyr::everything(), 
                      names_to = "name", 
                      values_to = "value") |> gluedown::md_table()
```

<br>

# Medicare Revalidation Clinic Group Practice Reassignment

<br>

```{r results='asis'}
provider_rcgpr(ex$number) |> 
  dplyr::mutate(dplyr::across(everything(), as.character)) |> 
  tidyr::pivot_longer(cols = dplyr::everything(), 
                      names_to = "name", 
                      values_to = "value") |> gluedown::md_table()
```


## Provider Statistics

These APIs are generally concerned with providing access to a provider's longitudinal utilization data.

### Physician & Other Practitioners

```{r results='asis', echo=FALSE}
gluedown::md_quote("by Provider and Service API")
```

```{r}
serv_ex <- purrr::map_dfr(as.character(2013:2020), 
                          ~physician_by_service(
                            npi = 1003000126, 
                            year = .x))
```

```{r results='asis', echo=FALSE}
serv_ex |> 
  dplyr::select(year, 
                hcpcs_cd, 
                tot_benes, 
                tot_srvcs, 
                avg_sbmtd_chrg, 
                avg_mdcr_alowd_amt, 
                avg_mdcr_pymt_amt) |> 
  gluedown::md_table()
```


> 2. by Geography and Service API:

<br>

```{r}
# mpop_geo_ex <- provider_mpop(hcpcs   = "99214", 
#                              set     = "geo",
#                              geo_lvl = "National",
#                              year    = "2020")
```

> 3. by Provider API:

<br>

```{r}
# mpop_prov_ex <- provider_mpop(npi  = npi, 
#                               set  = "prov",
#                               year = "2020")
```

### Medicare Monthly Enrollment

```{r echo=TRUE}
month_ex <- monthly_enroll(year      = 2018, 
                           month     = "Year", 
                           geo_lvl   = "County", 
                           state_abb = "AL", 
                           county    = "Autauga")
```


```{r results='asis', echo=FALSE}
gluedown::md_table(month_ex[, 1:7])
gluedown::md_blank()
gluedown::md_table(month_ex[, 8:13])
gluedown::md_blank()
gluedown::md_table(month_ex[, 14:18])
gluedown::md_blank()
gluedown::md_table(month_ex[, 19:22])
```

------------------------------------------------------------------------------

## Code of Conduct

Please note that the provider project is released with a [Contributor Code of Conduct](https://andrewallenbruce.github.io/provider/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
