---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

# `provider` <img src="man/figures/logo.svg" align="right" height="200" />

<!-- badges: start -->
[![R-CMD-check](https://github.com/andrewallenbruce/provider/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/provider/actions/workflows/R-CMD-check.yaml)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![License: MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://choosealicense.com/licenses/mit/)
[![code size](https://img.shields.io/github/languages/code-size/andrewallenbruce/provider.svg)](https://github.com/andrewallenbruce/provider)
[![last commit](https://img.shields.io/github/last-commit/andrewallenbruce/provider.svg)](https://github.com/andrewallenbruce/provider/commits/main)
[![Codecov test coverage](https://codecov.io/gh/andrewallenbruce/provider/branch/main/graph/badge.svg)](https://app.codecov.io/gh/andrewallenbruce/provider?branch=main)
[![CodeFactor](https://www.codefactor.io/repository/github/andrewallenbruce/provider/badge)](https://www.codefactor.io/repository/github/andrewallenbruce/provider)
<!-- badges: end -->

> Providing easy access to [healthcare provider](https://en.wikipedia.org/wiki/Health_care_provider)-centric data through publicly available APIs & sources.
 
<br>

```{r results='asis', echo=FALSE}
nppes_func <- gluedown::md_code("nppes_npi()")
nppes_link <- gluedown::md_link("NPPES National Provider Identifier (NPI) Registry" = "https://npiregistry.cms.hhs.gov/search")

open_func <- gluedown::md_code("open_payments()")
open_link <- gluedown::md_link("CMS Open Payments Program" = "https://openpaymentsdata.cms.gov/dataset/0380bbeb-aea1-58b6-b708-829f92a48202")

mppe_func  <- gluedown::md_code("provider_enrollment()")
mppe_link  <- gluedown::md_link("Medicare Fee-For-Service Public Provider Enrollment" = "https://data.cms.gov/provider-characteristics/medicare-provider-supplier-enrollment/medicare-fee-for-service-public-provider-enrollment")

mme_func   <- gluedown::md_code("beneficiary_enrollment()")
mme_link   <- gluedown::md_link("Medicare Monthly Enrollment" = "https://data.cms.gov/summary-statistics-on-beneficiary-enrollment/medicare-and-medicaid-reports/medicare-monthly-enrollment")

miss_func  <- gluedown::md_code("missing_information()")
miss_link  <- gluedown::md_link("CMS Public Reporting of Missing Digital Contact Information" = "https://data.cms.gov/provider-compliance/public-reporting-of-missing-digital-contact-information")

order_func <- gluedown::md_code("order_refer()")
order_link <- gluedown::md_link("Medicare Order and Referring" = "https://data.cms.gov/provider-characteristics/medicare-provider-supplier-enrollment/order-and-referring")

opt_func   <- gluedown::md_code("opt_out()")
opt_link   <- gluedown::md_link("Medicare Opt Out Affidavits" = "https://data.cms.gov/provider-characteristics/medicare-provider-supplier-enrollment/opt-out-affidavits")

pbp_link   <- gluedown::md_link("Medicare Physician & Other Practitioners: by Provider" = "https://data.cms.gov/provider-summary-by-type-of-service/medicare-physician-other-practitioners/medicare-physician-other-practitioners-by-provider")
pbp_func   <- gluedown::md_code("physician_by_provider()")

pbs_link   <- gluedown::md_link("Medicare Physician & Other Practitioners: by Provider and Service" = "https://data.cms.gov/provider-summary-by-type-of-service/medicare-physician-other-practitioners/medicare-physician-other-practitioners-by-provider-and-service")
pbs_func   <- gluedown::md_code("physician_by_service()")

pbg_link   <- gluedown::md_link("Medicare Physician & Other Practitioners: by Geography and Service" = "https://data.cms.gov/provider-summary-by-type-of-service/medicare-physician-other-practitioners/medicare-physician-other-practitioners-by-geography-and-service")
pbg_func   <- gluedown::md_code("physician_by_geography()")

redd_func  <- gluedown::md_code("revalidation_date()")
redd_link  <- gluedown::md_link("Medicare Revalidation Due Date" = "https://data.cms.gov/provider-characteristics/medicare-provider-supplier-enrollment/revalidation-due-date-list")

rere_func  <- gluedown::md_code("revalidation_reassign()")
rere_link  <- gluedown::md_link("Medicare Revalidation Reassignment" = "https://data.cms.gov/provider-characteristics/medicare-provider-supplier-enrollment/revalidation-reassignment-list")

recl_func  <- gluedown::md_code("revalidation_group()")
recl_link  <- gluedown::md_link("Medicare Revalidation Clinic Group Practice Reassignment" = "https://data.cms.gov/provider-characteristics/medicare-provider-supplier-enrollment/revalidation-clinic-group-practice-reassignment")

ccs_func   <- gluedown::md_code("cc_specific()")
ccs_link   <- gluedown::md_link("Medicare Specific Chronic Conditions" = "https://data.cms.gov/medicare-chronic-conditions/specific-chronic-conditions")

ccm_func   <- gluedown::md_code("cc_multiple()")
ccm_link   <- gluedown::md_link("Medicare Multiple Chronic Conditions" = "https://data.cms.gov/medicare-chronic-conditions/multiple-chronic-conditions")

clia_func  <- gluedown::md_code("clia_labs()")
clia_link  <- gluedown::md_link("Medicare Provider of Services File - Clinical Laboratories" = "https://data.cms.gov/provider-characteristics/hospitals-and-other-facilities/provider-of-services-file-clinical-laboratories")

tax_func   <- gluedown::md_code("taxonomy_crosswalk()")
tax_link   <- gluedown::md_link("Medicare Provider and Supplier Taxonomy Crosswalk" = "https://data.cms.gov/provider-characteristics/medicare-provider-supplier-enrollment/medicare-provider-and-supplier-taxonomy-crosswalk")

gluedown::md_table(data.frame(
  Function = c(nppes_func, 
               open_func,
               mppe_func, 
               mme_func,
               order_func,
               opt_func,
               pbp_func,
               pbs_func,
               pbg_func,
               redd_func,
               recl_func,
               rere_func,
               ccs_func,
               ccm_func,
               clia_func,
               tax_func,
               miss_func
               ), 
  API      = c(nppes_link, 
               open_link,
               mppe_link,
               mme_link,
               order_link,
               opt_link,
               pbp_link,
               pbs_link,
               pbg_link,
               redd_link,
               recl_link,
               rere_link,
               ccs_link,
               ccm_link,
               clia_link,
               tax_link,
               miss_link
               )))
```

<br>

## Installation

You can install the development version of `provider` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andrewallenbruce/provider")

# install.packages("remotes")
remotes::install_github("andrewallenbruce/provider")
```

```{r echo=TRUE}
# Load library
library(provider)
```

<br>

## Motivation

<br>

This package is primarily focused on accessing public API data that can be linked together via a healthcare provider's National Provider Identifier (NPI). Thus far, none of the APIs require the creation of a user account or API key. The data tend to fall into (and sometimes between) one of two categories: informational/operational and analytical. It only gets interesting when you start to link them together.

<br>

## NPPES NPI Registry API

```{r results='asis', echo=TRUE}
 # NPI-1
npi_1 <- nppes_npi(npi = 1710975040)

npi_1 |> dplyr::select(datetime:state) |> gluedown::md_table()
```

<br>

```{r results='asis', echo=TRUE}
npi_1 |> 
  dplyr::select(basic) |> 
  tidyr::unnest(basic) |> 
  tidyr::pivot_longer(dplyr::everything()) |> 
  gluedown::md_table()
```

<br>

```{r results='asis', echo=TRUE}
npi_1 |> 
  dplyr::select(taxonomies) |> 
  tidyr::unnest(taxonomies) |> 
  gluedown::md_table()
```

<br>

```{r results='asis', echo=TRUE}
npi_1 |> 
  dplyr::select(addresses) |> 
  tidyr::unnest(addresses) |> 
  gluedown::md_table()
```

<br>

```{r results='asis', echo=TRUE}
npi_1 |> 
  dplyr::select(identifiers) |> 
  tidyr::unnest(identifiers) |> 
  gluedown::md_table()
```

<br>


```{r results='asis', echo=TRUE}
 # NPI-2
npi_2 <- nppes_npi(npi = 1336413418)

npi_2 |> dplyr::select(datetime:state) |> 
  gluedown::md_table()

npi_2 |> 
  dplyr::select(basic) |> 
  tidyr::unnest(basic) |> 
  tidyr::pivot_longer(dplyr::everything()) |> 
  gluedown::md_table()

npi_2 |> 
  dplyr::select(taxonomies) |> 
  tidyr::unnest(taxonomies) |> 
  gluedown::md_table()

npi_2 |> 
  dplyr::select(addresses) |> 
  tidyr::unnest(addresses) |> 
  gluedown::md_table()
```

<br>

```{r results='asis', echo=TRUE}
 # Deactivated
nppes_npi(npi = 1659781227) |> 
  tidyr::unnest(cols = c(errors)) |> 
  gluedown::md_table()
```


<br><br>

## CMS Open Payments API

```{r}
op <- open_payments(recipient_npi = 1043218118)
```

<br><br>

```{r results='asis', echo=TRUE}
op |> tidyr::hoist(covered_recipient, 
                   recipient_npi = "covered_recipient_npi",
                   profile_id = "covered_recipient_profile_id",
                   first_name = "covered_recipient_first_name", 
                   last_name = "covered_recipient_last_name",
                   credential = "covered_recipient_primary_type_1",) |> 
      tidyr::hoist(recipient_address, 
                   city = "recipient_city", 
                   state = "recipient_state") |> 
      dplyr::select(program_year, 
                    recipient_npi, 
                    profile_id,
                    first_name,
                    last_name,
                    credential,
                    city,
                    state) |> 
      dplyr::slice_head() |> 
      gluedown::md_table()
```

<br><br>

```{r results='asis', echo=TRUE}
op_2 <- op |> tidyr::hoist(applicable_mfg_gpo, 
                           manufacturer_gpo_paying = "applicable_manufacturer_or_applicable_gpo_making_payment_name") |>
             tidyr::hoist(associated_drug_device, 
                          type = "indicate_drug_or_biological_or_device_or_medical_supply_1",
                          therapeutic_category = "product_category_or_therapeutic_area_1",
                          name = "name_of_drug_or_biological_or_device_or_medical_supply_1") |> 
             dplyr::select(payment_date = date_of_payment, 
                          manufacturer_gpo_paying,
                          type, 
                          name,
                          therapeutic_category,
                          payment_total = total_amount_of_payment_usdollars,
                          nature_of_payment = nature_of_payment_or_transfer_of_value) |> 
             dplyr::arrange(payment_date)

op_2 |> dplyr::mutate(nature_of_payment = stringr::str_trunc(nature_of_payment, 20, "right"),
                      manufacturer_gpo_paying = stringr::str_trunc(manufacturer_gpo_paying, 20, "right"),
                      name = stringr::str_trunc(name, 20, "right"),
                      therapeutic_category = stringr::str_trunc(therapeutic_category, 20, "right")) |> gluedown::md_table()
```


<br><br>

```{r results='asis', echo=TRUE}
op_2 |> 
  dplyr::group_by(manufacturer_gpo_paying, nature_of_payment, name) |> 
  dplyr::summarise(n = dplyr::n(),
                   payment_total = sum(payment_total), .groups = "drop") |> 
  dplyr::mutate(nature_of_payment = stringr::str_trunc(nature_of_payment, 20, "right")) |> 
  dplyr::arrange(dplyr::desc(payment_total)) |> 
  gluedown::md_table()
```


## CMS Missing Digital Contact Information API

```{r results='asis', echo=TRUE}
provider::missing_information(npi = 1144224569) |> gluedown::md_table()
```


<br>

### Medicare Fee-For-Service Public Provider Enrollment API

```{r}
prven <- tibble::tribble(
~fn,         ~params,
"provider_enrollment", list(npi = 1083879860),
"provider_enrollment", list(first_name = "MICHAEL", middle_name = "K", last_name = "GREENBERG", state = "MD"),
"provider_enrollment", list(org_name = "LUMINUS DIAGNOSTICS LLC", state = "GA"),
)

purrr::invoke_map_dfr(prven$fn, prven$params)
```


<br>

### Medicare Monthly Enrollment API

```{r}
months <- tibble::enframe(month.name) |> 
  dplyr::select(-name) |> 
  dplyr::slice(1:7) |> 
  tibble::deframe()

purrr::map_dfr(months, ~beneficiary_enrollment(year = 2022, geo_level = "State", state = "Georgia", month = .x))
```


<br>

### Medicare Order and Referring API

```{r results='asis', echo=TRUE}
provider::order_refer(npi = 1083879860) |> 
  gluedown::md_table()
```


<br>

### Medicare Opt-Out Affidavits API

```{r results='asis', echo=TRUE}
provider::opt_out(last = "Aaron") |> 
  gluedown::md_table()
```

<br>

### Medicare Provider and Supplier Taxonomy Crosswalk API

```{r results='asis', echo=TRUE}
provider::taxonomy_crosswalk(specialty_desc = "Rehabilitation Agency")
```

<br>

### Medicare Revalidation Due Date API

```{r results='asis', echo=TRUE}
provider::revalidation_date(npi = 1710912209)
```
<br>

### Medicare Revalidation Reassignment List API

```{r results='asis', echo=TRUE}
provider::revalidation_reassign(ind_npi = 1710912209)
```

<br>

### Medicare Revalidation Clinic Group Practice Reassignment API

```{r results='asis', echo=TRUE}
provider::revalidation_group(ind_npi = 1710912209)
```

<br>

### Medicare Physician & Other Practitioners APIs

<br>

> 1. by Provider and Service API:

<br>

```{r results='asis', echo=TRUE}
pbs <- purrr::map_dfr(2013:2020, ~physician_by_service(npi = 1003000126, year = .x))
```

<br>

> 2. by Geography and Service API:

<br>

```{r results='asis', echo=TRUE}
srvcs <- physician_by_service(npi = 1003000126, year = 2020)

srvcs |> tidyr::unnest(cols = c(rndrng_prvdr, totals_srvcs, hcpcs, averages))
```

<br>

```{r results='asis', echo=TRUE}
purrr::map_dfr(service$hcpcs_cd, ~physician_by_geography(geo_level = "National", year = 2020, hcpcs_code = .x)) |> 
  terse::terse(config = list(ansi = FALSE), width = 100)
```

<br>

```{r results='asis', echo=TRUE}
purrr::map_dfr(service$hcpcs_cd, ~physician_by_geography(geo_desc = "Maryland", year = 2020, hcpcs_code = .x)) |> 
  terse::terse(config = list(ansi = FALSE), width = 100)
```

<br>

> 3. by Provider API:

<br>

```{r results='asis', echo=TRUE}
x <- purrr::map_dfr(as.character(2013:2020), ~physician_by_provider(npi = 1003000126, year = .x))
```

<br>

```{r results='asis', echo=TRUE}
x |> dplyr::select(rndrng_npi, rndrng_prvdr) |> 
     tidyr::unnest(cols = c(rndrng_prvdr)) |> 
     dplyr::slice_head() |> 
     tidyr::pivot_longer(cols = dplyr::everything()) |> 
     gluedown::md_table()
```

<br>

```{r results='asis', echo=TRUE}
x |> dplyr::select(year, totals_srvcs) |> 
     tidyr::unnest(cols = c(totals_srvcs)) |> 
     gluedown::md_table()
```

<br>

```{r results='asis', echo=TRUE}
x |> dplyr::select(year, bene_age) |> 
     tidyr::unnest(cols = c(bene_age)) |> 
     gluedown::md_table()
```

<br>

```{r results='asis', echo=TRUE}
x |> dplyr::select(year, bene_sex, bene_status) |> 
     tidyr::unnest(cols = c(bene_sex, bene_status)) |> 
     gluedown::md_table()
```

<br>

```{r results='asis', echo=TRUE}
x |> dplyr::select(year, bene_race) |> 
     tidyr::unnest(cols = c(bene_race)) |> 
     gluedown::md_table()
```

<br>

```{r results='asis', echo=TRUE}
x |> dplyr::select(year, bene_cc) |> 
     tidyr::unnest(cols = c(bene_cc)) |> 
     gluedown::md_table()
```

<br>

### Medicare Multiple Chronic Conditions API

```{r results='asis', echo=TRUE}
cc_multiple(year = 2007, geo_lvl = "National", demo_lvl = "Race")
```

<br>

### Medicare Specific Chronic Conditions API

```{r results='asis', echo=TRUE}
cc_specific(year = 2007, geo_lvl = "National", demo_lvl = "Race")
```

<br>

------------------------------------------------------------------------------

## Code of Conduct

Please note that the provider project is released with a [Contributor Code of Conduct](https://andrewallenbruce.github.io/provider/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
