---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `provider` <img src="man/figures/logo.svg" align="right" height="500" />

<!-- badges: start -->
[![R-CMD-check](https://github.com/andrewallenbruce/provider/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/provider/actions/workflows/R-CMD-check.yaml)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![License: MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://choosealicense.com/licenses/mit/)
<!-- badges: end -->

The goal of {provider} is to provide performant and reliable open-source tools to facilitate easy access to [healthcare provider](https://en.wikipedia.org/wiki/Health_care_provider) data through publicly available APIs & sources.

## Installation

You can install the development version of `provider` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andrewallenbruce/provider")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(provider)
## basic example code
```


## Code of Conduct

Please note that the provider project is released with a [Contributor Code of Conduct](https://andrewallenbruce.github.io/provider/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
