---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r}
#| label: setup
#| include: FALSE
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE,
  message   = TRUE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "",
  fig.path = "man/figures/README-",
  out.width = "100%"
  )
library(tibble)
```

# <b>provider</b> <a href="https://andrewallenbruce.github.io/provider/"><img src="man/figures/logo.svg" align="right" height="139" alt="provider website" /></a>

> <b>Tidy Healthcare Provider API Interface</b>

<!-- badges: start -->
[![Ask DeepWiki](https://deepwiki.com/badge.svg)](https://deepwiki.com/andrewallenbruce/provider)
[![zread](https://img.shields.io/badge/Ask_Zread-_.svg?style=flat&color=00b0aa&labelColor=000000&logo=data%3Aimage%2Fsvg%2Bxml%3Bbase64%2CPHN2ZyB3aWR0aD0iMTYiIGhlaWdodD0iMTYiIHZpZXdCb3g9IjAgMCAxNiAxNiIgZmlsbD0ibm9uZSIgeG1sbnM9Imh0dHA6Ly93d3cudzMub3JnLzIwMDAvc3ZnIj4KPHBhdGggZD0iTTQuOTYxNTYgMS42MDAxSDIuMjQxNTZDMS44ODgxIDEuNjAwMSAxLjYwMTU2IDEuODg2NjQgMS42MDE1NiAyLjI0MDFWNC45NjAxQzEuNjAxNTYgNS4zMTM1NiAxLjg4ODEgNS42MDAxIDIuMjQxNTYgNS42MDAxSDQuOTYxNTZDNS4zMTUwMiA1LjYwMDEgNS42MDE1NiA1LjMxMzU2IDUuNjAxNTYgNC45NjAxVjIuMjQwMUM1LjYwMTU2IDEuODg2NjQgNS4zMTUwMiAxLjYwMDEgNC45NjE1NiAxLjYwMDFaIiBmaWxsPSIjZmZmIi8%2BCjxwYXRoIGQ9Ik00Ljk2MTU2IDEwLjM5OTlIMi4yNDE1NkMxLjg4ODEgMTAuMzk5OSAxLjYwMTU2IDEwLjY4NjQgMS42MDE1NiAxMS4wMzk5VjEzLjc1OTlDMS42MDE1NiAxNC4xMTM0IDEuODg4MSAxNC4zOTk5IDIuMjQxNTYgMTQuMzk5OUg0Ljk2MTU2QzUuMzE1MDIgMTQuMzk5OSA1LjYwMTU2IDE0LjExMzQgNS42MDE1NiAxMy43NTk5VjExLjAzOTlDNS42MDE1NiAxMC42ODY0IDUuMzE1MDIgMTAuMzk5OSA0Ljk2MTU2IDEwLjM5OTlaIiBmaWxsPSIjZmZmIi8%2BCjxwYXRoIGQ9Ik0xMy43NTg0IDEuNjAwMUgxMS4wMzg0QzEwLjY4NSAxLjYwMDEgMTAuMzk4NCAxLjg4NjY0IDEwLjM5ODQgMi4yNDAxVjQuOTYwMUMxMC4zOTg0IDUuMzEzNTYgMTAuNjg1IDUuNjAwMSAxMS4wMzg0IDUuNjAwMUgxMy43NTg0QzE0LjExMTkgNS42MDAxIDE0LjM5ODQgNS4zMTM1NiAxNC4zOTg0IDQuOTYwMVYyLjI0MDFDMTQuMzk4NCAxLjg4NjY0IDE0LjExMTkgMS42MDAxIDEzLjc1ODQgMS42MDAxWiIgZmlsbD0iI2ZmZiIvPgo8cGF0aCBkPSJNNCAxMkwxMiA0TDQgMTJaIiBmaWxsPSIjZmZmIi8%2BCjxwYXRoIGQ9Ik00IDEyTDEyIDQiIHN0cm9rZT0iI2ZmZiIgc3Ryb2tlLXdpZHRoPSIxLjUiIHN0cm9rZS1saW5lY2FwPSJyb3VuZCIvPgo8L3N2Zz4K&logoColor=ffffff)](https://zread.ai/andrewallenbruce/provider)
[![Codecov test coverage](https://codecov.io/gh/andrewallenbruce/provider/branch/main/graph/badge.svg)](https://app.codecov.io/gh/andrewallenbruce/provider?branch=main)
[![CodeFactor](https://www.codefactor.io/repository/github/andrewallenbruce/provider/badge)](https://www.codefactor.io/repository/github/andrewallenbruce/provider)
[![code size](https://img.shields.io/github/languages/code-size/andrewallenbruce/provider.svg)](https://github.com/andrewallenbruce/provider)
<!-- badges: end -->

You can install `provider` from [GitHub](https://github.com/) with:

```r
# install.packages("pak")
pak::pak("andrewallenbruce/provider")
```

## Overview

The `provider` package is a high-level interface designed to streamline access 
to publicly available healthcare provider data from the Centers for Medicare and
Medicaid Services (CMS) and other federal sources. It provides a unified, tidy
framework for querying complex datasets that are essential for medical coding,
billing, and healthcare revenue cycle management.

The provider package is a technical interface for accessing publicly available
healthcare provider data from the Centers for Medicare and Medicaid Services
(CMS) and the Health Resources and Services Administration (HRSA). It provides a
unified, tidy API for querying complex datasets such as the NPPES NPI Registry,
PECOS enrollment data, and hospital transparency records.

## Purpose & Scope

Navigating the healthcare data ecosystem often involves disparate APIs with
inconsistent field names and data structures. `provider` abstracts these
complexities into a consistent set of R functions that return "tidy" data
frames.

The package targets several key data domains:

   - __Individual Providers__: Clinician demographics, enrollments, and opt-out affidavits
   - __Organizational Providers__: Hospital data, CLIA labs, and Rural Health Clinics (RHC)
   - __Compliance & Sanctions__: Medicare revocations and hospital price transparency enforcement
   - __General Registry__: NPPES NPI registry and reassignment of benefits

### :rocket: Basic Usage Patterns

Most functions in `provider` follow a similar pattern: they accept identifiers
(like an `npi`) or search criteria (like an `org_name`) and return a `tibble`.

#### Query Modifiers

`provider` supports query modifiers for more precise filtering. These are
implemented as Modifier S7 classes

```{r}
#| label: load
#| echo: TRUE
#| message: TRUE
#| warning: FALSE
library(provider)
```

#### :office: Facility Affiliations

```{r}
#| label: affiliation
affiliations(facility_ccn = 110122)
```

#### :handshake: Reassignment of Benefits

```{r}
#| label: reassignment
reassignments(
  org_name = starts("SGMC"),
  state = "GA")
```

#### :-1: Revoked Medicare Providers

```{r}
#| label: revoked
revocations(state = "GA")
```

#### :identification_card: Clinician Demographics

```{r}
#| label: clinician
clinicians(
  org_name = starts("SGMC"),
  org_state = "GA")
```

##### :outbox_tray: Opt-Out Affidavits

```{r}
#| label: opted_out
opt_out(
  first = starts("B"),
  specialty = starts("Oral"))
```

##### :receipt: Order & Referral Eligibility

```{r}
#| label: order_refer
order_refer(
  first = contains("LESS"),
  ptb = TRUE,
  hospice = FALSE,
  hha = FALSE)
```

##### :health_worker: Medicare Enrollments

```{r}
#| label: enrolled
providers(
  org_name = starts("SGMC"),
  state = "GA")
```

##### :calendar: Pending Enrollments

```{r}
#| label: pending
pending(
  first = contains("A"),
  last = ends("E"))
```

##### :hospital: Medicare Hospitals

```{r}
#| label: hospital
hospitals(ccn = "110122")
```

##### :test_tube: CLIA Laboratories

```{r}
#| label: clia
clia(
  facility_name = starts("SGMC"),
  state = "GA")
```

##### :mag_right: Hospital Transparency Enforcement

```{r}
#| label: transparency
transparency(
  action = "closure", 
  state = "WA")
```

------------------------------------------------------------------------------

### :balance_scale: Code of Conduct

Please note that the **`provider`** project is released with a [Contributor Code of Conduct](https://andrewallenbruce.github.io/provider/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.


### :classical_building: Governance

This project is primarily maintained by [Andrew Bruce](https://github.com/andrewallenbruce). Other authors may occasionally assist with some of these duties.
