---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE,
  message   = TRUE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 600, 
  out.width = "100%"
  )
```

# provider <img src="man/figures/logo.svg" align="right" height="200" />

>  Providing easy access to [healthcare provider](https://en.wikipedia.org/wiki/Health_care_provider) data through publicly available APIs.

<!-- badges: start -->
[![R-CMD-check](https://github.com/andrewallenbruce/provider/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/provider/actions/workflows/R-CMD-check.yaml)
[![License: MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://choosealicense.com/licenses/mit/)
[![code size](https://img.shields.io/github/languages/code-size/andrewallenbruce/provider.svg)](https://github.com/andrewallenbruce/provider)
[![last commit](https://img.shields.io/github/last-commit/andrewallenbruce/provider.svg)](https://github.com/andrewallenbruce/provider/commits/main)
[![Codecov test coverage](https://codecov.io/gh/andrewallenbruce/provider/branch/main/graph/badge.svg)](https://app.codecov.io/gh/andrewallenbruce/provider?branch=main)
[![CodeFactor](https://www.codefactor.io/repository/github/andrewallenbruce/provider/badge)](https://www.codefactor.io/repository/github/andrewallenbruce/provider)
<!-- badges: end -->



## :package: Installation

You can install __`provider`__ from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("andrewallenbruce/provider")
```

## :beginner: Usage

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(provider)
library(dplyr)
library(tidyr)
```


### `affiliations()`

```{r}
affiliations(npi = 1023630738, 
             pac = 9032521372, 
             facility_ccn = 370781) |> 
  glimpse()
```


### `beneficiaries()`

```{r}
beneficiaries(year   = 2024, 
              period = "Month", 
              level  = "County", 
              state  = "GA", 
              county = "Lowndes County") |> 
  glimpse()
```

### `clinicians()`

```{r}
clinicians(npi = 1932365699) |> 
  glimpse()
```

### `hospitals()`

```{r}
hospitals(npi = 1720098791) |> 
  glimpse()
```

### `laboratories()`

```{r}
laboratories(clia = "11D0265516") |> 
  glimpse()
```


### `nppes()`

```{r}
nppes(npi = 1497535637) |> 
  glimpse()
```


### `open_payments()`

```{r}
open_payments(year  = 2021, 
              npi   = 1023630738, 
              na.rm = TRUE) |> 
  glimpse()
```


### `opt_out()`

```{r}
opt_out(npi = 1043522824) |> 
  glimpse()
```


### `order_refer()`

```{r}
order_refer(npi = 1043522824, tidy = FALSE) |> 
  glimpse()
```


### `outpatient()`

```{r}
outpatient(year  = 2021, 
           state = "GA", 
           city  = "Valdosta", 
           apc   = "5072") |> 
  glimpse()
```


### `prescribers()`

```{r}
prescribers(year = 2019, 
            type = 'Provider', 
            npi = 1003000126) |> 
  glimpse()
```


```{r}
prescribers(year = 2019, 
            npi = 1003000126,
            type = 'Drug',
            brand_name = 'Atorvastatin Calcium') |> 
  glimpse()
```


```{r}
prescribers(year = 2021, 
            type = 'Geography',
            level = 'National',
            brand_name = 'Clotrimazole-Betamethasone') |> 
  glimpse()
```


### `providers()`

```{r}
providers(npi  = 1720098791, 
          enid = "O20040610001257") |> 
  glimpse()
```

### `quality_payment()`

```{r}
quality_payment(year = 2021, 
                npi  = 1932365699) |> 
  glimpse()
```


```{r}
q <- quality_payment(year = 2021, 
                     npi = 1932365699)

q |> 
  select(
    year,
    qpp_status
    ) |> 
  unnest(qpp_status)
```


```{r}
q |> 
  select(
    year,
    qpp_measures
    ) |> 
  unnest(qpp_measures)
```

### `quality_eligibility()`

```{r}
quality_eligibility(year = 2021, 
                    npi  = 1932365699) |> 
  glimpse()
```

### `reassignments()`

```{r}
reassignments(npi = 1932365699, 
              pac_org = 7719037548) |> 
  glimpse()
```


### `utilization()`

```{r}
utilization(year = 2021, 
            npi  = 1932365699, 
            type = "Provider") |> 
  glimpse()
```



```{r}
p <- utilization(year = 2021, 
                 npi = 1932365699, 
                 type = "Provider")

select(p, year, performance) |> 
  unnest(performance) |> 
  glimpse()
```


```{r}
select(p, year, demographics) |> 
  unnest(demographics) |> 
  glimpse()
```


```{r}
select(p, year, conditions) |> 
  unnest(conditions) |> 
  glimpse()
```



```{r}
utilization(year  = 2021, 
            npi   = 1932365699,
            hcpcs = "99214",
            type  = "Service") |> 
  glimpse()
```


```{r}
utilization(year  = 2021, 
            hcpcs = "99205", 
            level = "National",
            pos   = "F",
            type  = "Geography") |> 
  glimpse()
```

------------------------------------------------------------------------------

## :balance_scale: Code of Conduct

Please note that the `provider` project is released with a [Contributor Code of Conduct](https://andrewallenbruce.github.io/provider/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.


## :classical_building: Governance

This project is primarily maintained by [Andrew Bruce](https://github.com/andrewallenbruce). Other authors may occasionally assist with some of these duties.
