---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE,
  message   = TRUE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "",
  fig.path = "man/figures/README-",
  out.width = "100%"
  )
library(tibble)
```

# <b>provider</b> <a href="https://andrewallenbruce.github.io/provider/"><img src="man/figures/logo.svg" align="right" height="139" alt="provider website" /></a>

> <b>Tidy Healthcare Provider API Interface</b>

<br>

<!-- badges: start -->

![GitHub R package version](https://img.shields.io/github/r-package/v/andrewallenbruce/provider?style=flat-square&logo=R&label=Package&color=%23192a38)
[![License: MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://choosealicense.com/licenses/mit/)
[![code size](https://img.shields.io/github/languages/code-size/andrewallenbruce/provider.svg)](https://github.com/andrewallenbruce/provider) <br>
[![last commit](https://img.shields.io/github/last-commit/andrewallenbruce/provider.svg)](https://github.com/andrewallenbruce/provider/commits/main)
[![Codecov test coverage](https://codecov.io/gh/andrewallenbruce/provider/branch/main/graph/badge.svg)](https://app.codecov.io/gh/andrewallenbruce/provider?branch=main)
[![CodeFactor](https://www.codefactor.io/repository/github/andrewallenbruce/provider/badge)](https://www.codefactor.io/repository/github/andrewallenbruce/provider)

<!-- badges: end -->


You can install `provider` from [GitHub](https://github.com/) with:

```r
# install.packages("pak")
pak::pak("andrewallenbruce/provider")
```

## :beginner: Usage

```{r echo=TRUE, message=TRUE, warning=FALSE}
library(provider)
```

#### Facility Affiliations

```{r}
affiliations(facility_ccn = 370781)
```

#### Reassignments

```{r}
reassignments(org_pac = 7719037548)
```

#### Revocations

```{r}
revocations(
  specialty = contains("CARDIO"), 
  state = not("TX")
  )
```

#### National Provider Catalog

```{r}
clinicians(
  city = any_of(c("Atlanta", "Macon")), 
  state = "GA", 
  gender = "F",
  year = 2025
  )
```

#### Opt-Out Affidavits

```{r}
opt_out(
  specialty = "Psychiatry", 
  order_refer = FALSE
  )
```

#### Order & Referral Eligibility

```{r}
order_refer(
  last = starts_with("B"),
  part_b = TRUE,
  dme = TRUE,
  hha = FALSE,
  pmd = TRUE,
  hospice = FALSE)
```

#### Pending Enrollments

```{r}
pending(
  first = starts_with("V"),
  last = starts_with("W")
  )
```

#### Provider Enrollment

```{r}
providers(
  first = contains("C"),
  state = "AK",
  spec = ends_with("30")
  )
```

#### Hospitals

```{r}
hospitals(
  city = "Atlanta",
  state = "GA",
  subgroup = subgroups(
    acute = FALSE,
    psych = TRUE
  )
)
```

#### CLIA Laboratories

```{r}
clia(name = starts_with("CDC"))
```

#### Hospital Transparency Enforcement

```{r}
transparency(action = contains("CMP"))
```

------------------------------------------------------------------------------

<br>

## :balance_scale: Code of Conduct

Please note that the `provider` project is released with a [Contributor Code of Conduct](https://andrewallenbruce.github.io/provider/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.


## :classical_building: Governance

This project is primarily maintained by [Andrew Bruce](https://github.com/andrewallenbruce). Other authors may occasionally assist with some of these duties.
