---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE,
  message   = TRUE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 600, 
  out.width = "100%"
  )
```

# provider <img src="man/figures/logo.svg" align="right" height="200" />

<!-- badges: start -->
[![R-CMD-check](https://github.com/andrewallenbruce/provider/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/provider/actions/workflows/R-CMD-check.yaml)
[![License: MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://choosealicense.com/licenses/mit/)
[![code size](https://img.shields.io/github/languages/code-size/andrewallenbruce/provider.svg)](https://github.com/andrewallenbruce/provider)
[![last commit](https://img.shields.io/github/last-commit/andrewallenbruce/provider.svg)](https://github.com/andrewallenbruce/provider/commits/main)
[![pkgdown](https://github.com/andrewallenbruce/provider/actions/workflows/pkgdown.yaml/badge.svg)](https://github.com/andrewallenbruce/provider/actions/workflows/pkgdown.yaml)
[![Codecov test coverage](https://codecov.io/gh/andrewallenbruce/provider/branch/main/graph/badge.svg)](https://app.codecov.io/gh/andrewallenbruce/provider?branch=main)
[![CodeFactor](https://www.codefactor.io/repository/github/andrewallenbruce/provider/badge)](https://www.codefactor.io/repository/github/andrewallenbruce/provider)
![GitHub milestone](https://img.shields.io/github/milestones/progress/andrewallenbruce/provider/1?color=white&logo=milestones)
<!-- badges: end -->

> Providing easy access to [healthcare provider](https://en.wikipedia.org/wiki/Health_care_provider) data through publicly available APIs.

## Installation

You can install __`provider`__ from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("andrewallenbruce/provider")
```

## Usage

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(provider)
library(dplyr)
library(tidyr)
```


### `affiliations()`

```{r}
affiliations(npi = 1023630738, facility_ccn = "37Z324") |> glimpse()
```


### `beneficiaries()`

```{r}
beneficiaries(year = 2022, 
              period = "Year", 
              level = "County", 
              state = "GA", 
              county = "Lowndes") |> 
  glimpse()
```

### `clinicians()`

```{r}
clinicians(npi = 1932365699) |> glimpse()
```

### `conditions()`

```{r}
conditions(year = 2018, 
           set = "multiple", 
           level = "national", 
           age = "all", 
           demo = "all", 
           mcc = "6+") |> 
  glimpse()
```


```{r}
conditions(year = 2018, 
           set = "specific", 
           level = "national", 
           age = "all", 
           demo = "all",
           condition = "Arthritis") |> 
  glimpse()
```

### `hospitals()`

```{r}
hospitals(npi = 1720098791) |> glimpse()
```

### `laboratories()`

```{r}
laboratories(clia = "11D0265516") |> glimpse()
```


### `nppes()`

```{r}
nppes(npi = 1720098791) |> glimpse()
```


### `open_payments()`

```{r}
open_payments(year = 2021, npi = 1023630738) |> 
  mutate(info = ndc_lookup(ndc), ndc = NULL) |> 
  unnest(info) |> glimpse()
```


### `opt_out()`

```{r}
opt_out(npi = 1043522824) |> glimpse()
```


### `order_refer()`

```{r}
order_refer(npi = 1043522824, 
            pivot = FALSE) |> glimpse()
```


### `outpatient()`

```{r}
outpatient(year = 2021, 
           state = "GA", 
           city = "Valdosta", 
           apc = "5072") |> glimpse()
```


### `providers()`

```{r}
providers(npi = 1720098791) |> glimpse()
```

### `quality_payment()`

```{r}
quality_payment(year = 2021, 
                npi = 1932365699) |> glimpse()
```


```{r}
q <- quality_payment(year = 2021, npi = 1932365699)

dplyr::select(q, year, statuses) |> 
  tidyr::unnest(statuses) 
```


```{r}
dplyr::select(q, year, measures) |> 
  tidyr::unnest(measures)
```

### `reassignments()`

```{r}
reassignments(npi = 1932365699) |> glimpse()
```


### `utilization()`

```{r}
utilization(year = 2021, 
            npi = 1932365699, 
            type = "provider") |> glimpse()
```



```{r}
p <- utilization(year = 2021, npi = 1932365699, type = "provider")

p$performance |> glimpse()
```


```{r}
p$demographics |> glimpse()
```


```{r}
p$conditions |> glimpse()
```



```{r}
utilization(year = 2021, 
            npi = 1932365699,
            hcpcs = "99214",
            type = "service") |> glimpse()
```


```{r}
utilization(year = 2021, 
            hcpcs = "99205", 
            level = "National",
            pos = "F",
            type = "geography") |> glimpse()
```

------------------------------------------------------------------------------

## Code of Conduct

Please note that the `provider` project is released with a [Contributor Code of Conduct](https://andrewallenbruce.github.io/provider/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

