---
title: "CMS API Notes"
editor_options: 
  chunk_output_type: console
output: 
  html_document: 
    toc: true
    toc_depth: 5
    highlight: zenburn
    theme: united
    keep_md: true
    df_print: tibble
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE, 
  message   = TRUE, 
  warning   = TRUE,
  error     = TRUE,
  comment   = "",
  dpi       = 300, 
  out.width = "100%"
)
library(tibble)
```


   - [data.CMS.gov API FAQ]("https://data.cms.gov/sites/default/files/2024-10/7ef65521-65a4-41ed-b600-3a0011f8ec4b/API%20Guide%20Formatted%201_6.pdf")

### Overview

   1. Dataset API endpoints have this structure:

      ```json
      https://data.cms.gov/data-api/v1/dataset/{{dataset_id}}/data
      ```

   2. The system uses the [JSONAPI](https://jsonapi.org/) query syntax:

      ```json
      ?filter[field_name]=value&filter[field_other]=value
      ```

<br>

### Examples

   - __EQUALS__:
   
      ```yaml
      dataset: "Medicare FFS Provider Enrollment"
        code: filter(PROVIDER_TYPE_DESC == "PRACTITIONER - GENERAL PRACTICE")
          query: >
             https://data.cms.gov/data-api/v1/dataset/
             2457ea29-fc82-48b0-86ec-3b0755de7515/data?
             filter[PROVIDER_TYPE_DESC]=PRACTITIONER%20-%20GENERAL%20PRACTICE
      ```
   - __CONTAINS__:
   
      ```yaml
      dataset: "Medicare FFS Provider Enrollment"
        code: grepl(PROVIDER_TYPE_DESC, "SUPPLIER")
          query: >
             https://data.cms.gov/data-api/v1/dataset/
             2457ea29-fc82-48b0-86ec-3b0755de7515/data?
             filter[example][condition][path]=PROVIDER_TYPE_DESC&
             filter[example][condition][operator]=CONTAINS&
             filter[example][condition][value]=SUPPLIER
      ```
   - __CONTAINS & EQUALS__:
   
      ```yaml
      dataset: "Medicare FFS Provider Enrollment"
        code: filter(STATE_CD == "MD" & grepl(PROVIDER_TYPE_DESC, "PRACTITIONER"))
          query: >
             https://data.cms.gov/data-api/v1/dataset/
             2457ea29-fc82-48b0-86ec-3b0755de7515/data?
             filter[filter-1][condition][path]=PROVIDER_TYPE_DESC&
             filter[filter-1][condition][operator]=CONTAINS&
             filter[filter-1][condition][value]=PRACTITIONER&
             filter[filter-2][condition][path]=STATE_CD&
             filter[filter-2][condition][operator]==&
             filter[filter-2][condition][value]=MD
      ```
<br>

### __Outputs__: `/data?` _vs._ `/data-viewer?`

`/data?` returns a `data.frame` with column names:

```{r}
paste0(
  "https://data.cms.gov/data-api/v1/dataset/",
  "2457ea29-fc82-48b0-86ec-3b0755de7515/data?",
  "filter[PROVIDER_TYPE_DESC]=PRACTITIONER%20-%20GENERAL%20PRACTICE"
) |> 
httr2::request() |> 
  httr2::req_perform() |> 
  provider:::parse_string() |> 
  fastplyr::as_tbl() |> 
  head()
```

While `/data-viewer?` returns a `matrix`, no column names:

```{r}
x <- paste0(
  "https://data.cms.gov/data-api/v1/dataset/",
  "2457ea29-fc82-48b0-86ec-3b0755de7515/data-viewer?",
  "filter[PROVIDER_TYPE_DESC]=PRACTITIONER%20-%20GENERAL%20PRACTICE"
) |> 
httr2::request() |> 
  httr2::req_perform() |> 
  provider:::parse_string()

fastplyr::new_tbl(
 npi = x$data[, 1],
 multi = x$data[, 2],
 pac = x$data[, 3],
 enid = x$data[, 4],
 pr_code = x$data[, 5],
 pr_type = x$data[, 6],
 state = x$data[, 7],
 first = x$data[, 8],
 middle = x$data[, 9],
 last = x$data[, 10],
 org = x$data[, 11]
)
```

<br>

> Also, requests with `%20` encoded spaces seem to be faster than those with `+` encoded spaces.

<br>
