---
title: "API Notes"
editor_options: 
  chunk_output_type: console
output: 
  html_document: 
    toc: true
    toc_depth: 5
    highlight: zenburn
    theme: united
    keep_md: true
    df_print: tibble
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE, 
  message   = TRUE, 
  warning   = TRUE,
  error     = TRUE,
  comment   = "",
  dpi       = 300, 
  out.width = "100%"
)
library(provider)
library(tibble)
```

## CMS

   - [data.CMS.gov API FAQ]("https://data.cms.gov/sites/default/files/2024-10/7ef65521-65a4-41ed-b600-3a0011f8ec4b/API%20Guide%20Formatted%201_6.pdf")

### Overview

   1. Dataset API endpoints have this structure:

      ```json
      https://data.cms.gov/data-api/v1/dataset/{{dataset_id}}/data
      ```

   2. The system uses the [JSONAPI](https://jsonapi.org/) query syntax:

      ```json
      ?filter[field_name]=value&filter[field_other]=value
      ```

<br>

### Examples

   - __EQUALS__:
   
      ```yaml
      dataset: "Medicare FFS Provider Enrollment"
        code: filter(PROVIDER_TYPE_DESC == "PRACTITIONER - GENERAL PRACTICE")
          query: >
             https://data.cms.gov/data-api/v1/dataset/
             2457ea29-fc82-48b0-86ec-3b0755de7515/data?
             filter[PROVIDER_TYPE_DESC]=PRACTITIONER%20-%20GENERAL%20PRACTICE
      ```
   - __CONTAINS__:
   
      ```yaml
      dataset: "Medicare FFS Provider Enrollment"
        code: grepl(PROVIDER_TYPE_DESC, "SUPPLIER")
          query: >
             https://data.cms.gov/data-api/v1/dataset/
             2457ea29-fc82-48b0-86ec-3b0755de7515/data?
             filter[example][condition][path]=PROVIDER_TYPE_DESC&
             filter[example][condition][operator]=CONTAINS&
             filter[example][condition][value]=SUPPLIER
      ```
   - __CONTAINS & EQUALS__:
   
      ```yaml
      dataset: "Medicare FFS Provider Enrollment"
        code: filter(STATE_CD == "MD" & grepl(PROVIDER_TYPE_DESC, "PRACTITIONER"))
          query: >
             https://data.cms.gov/data-api/v1/dataset/
             2457ea29-fc82-48b0-86ec-3b0755de7515/data?
             filter[filter-1][condition][path]=PROVIDER_TYPE_DESC&
             filter[filter-1][condition][operator]=CONTAINS&
             filter[filter-1][condition][value]=PRACTITIONER&
             filter[filter-2][condition][path]=STATE_CD&
             filter[filter-2][condition][operator]==&
             filter[filter-2][condition][value]=MD
      ```
<br>

### __Outputs__: `/data?` _vs._ `/data-viewer?`

`/data?` returns a `data.frame` with column names:

```{r}
paste0(
  "https://data.cms.gov/data-api/v1/dataset/",
  "2457ea29-fc82-48b0-86ec-3b0755de7515/data?",
  "filter[PROVIDER_TYPE_DESC]=PRACTITIONER%20-%20GENERAL%20PRACTICE"
) |> 
httr2::request() |> 
  httr2::req_perform() |> 
  provider:::parse_string() |> 
  fastplyr::as_tbl() |> 
  head()
```

While `/data-viewer?` returns a `matrix`, no column names:

```{r}
x <- paste0(
  "https://data.cms.gov/data-api/v1/dataset/",
  "2457ea29-fc82-48b0-86ec-3b0755de7515/data-viewer?",
  "filter[PROVIDER_TYPE_DESC]=PRACTITIONER%20-%20GENERAL%20PRACTICE"
) |> 
httr2::request() |> 
  httr2::req_perform() |> 
  provider:::parse_string()

fastplyr::new_tbl(
 npi = x$data[, 1],
 multi = x$data[, 2],
 pac = x$data[, 3],
 enid = x$data[, 4],
 pr_code = x$data[, 5],
 pr_type = x$data[, 6],
 state = x$data[, 7],
 first = x$data[, 8],
 middle = x$data[, 9],
 last = x$data[, 10],
 org = x$data[, 11]
)
```

<br>

> Also, requests with `%20` encoded spaces seem to be faster than those with `+` encoded spaces.

<br>

## Provider

Which query modifiers work?

```{r}
clinicians(first = starts_with("J")) |> _$first |> collapse::funique()
clinicians(first = contains("J"), count = TRUE)
```


```{r}
url <- paste0(
  "https://data.cms.gov/provider-data/api/1/datastore/query/mj5m-pzi6/0?",
  "schema=false&",
  "keys=true&",
  "results=true&",
  "count=true&",
  "format=json&",
  "rowIds=false&",
  "limit=10&",
  "offset=0&",
  "conditions[0][property]=provider_first_name&",
  "conditions[0][operator]=contains&",
  "conditions[0][value]=JO"
)
# contains
url |> 
  urlparse::url_encoder(safe = ":/=&?") |> 
  httr2::request() |> 
  httr2::req_perform() |> 
  provider:::parse_string() |> 
  _$results |> 
  _$provider_first_name |> 
  collapse::funique()
# starts with
url |> 
  httr2::url_modify_query(
    `conditions[0][operator]` = "starts with") |> 
  httr2::request() |> 
  httr2::req_perform() |> 
  provider:::parse_string() |> 
  _$results |> 
  _$provider_first_name |> 
  collapse::funique()
# ENDS_WITH
url |> 
  httr2::url_modify_query(
    `conditions[0][operator]` = "ENDS_WITH") |> 
  httr2::request() |> 
  httr2::req_perform() |> 
  provider:::parse_string() |> 
  _$results |> 
  _$provider_first_name |> 
  collapse::funique()
# =
url |> 
  httr2::url_modify_query(
    `conditions[0][operator]` = "=") |> 
  httr2::request() |> 
  httr2::req_perform() |> 
  provider:::parse_string() |> 
  _$results |> 
  _$provider_first_name |> 
  collapse::funique()
# like
url |> 
  httr2::url_modify_query(
    `conditions[0][operator]` = "like") |> 
  httr2::request() |> 
  httr2::req_perform() |> 
  provider:::parse_string() |> 
  _$results |> 
  _$provider_first_name |> 
  collapse::funique()
```


## Refactoring the URL building process

   - CMS API

```{r}
cms <- list(
  uri = "https://data.cms.gov/data-api/v1/dataset/<<uuid>>/data<<end>>",
  uid = "2457ea29-fc82-48b0-86ec-3b0755de7515",
  end = list(stats = "/stats?", qmk = "?"),
  opt = list(size = 10, offset = 0)
)

query = "filter[PROVIDER_TYPE_DESC]=PRACTITIONER%20-%20GENERAL%20PRACTICE"

# Total Row Count
paste0(cms$uri, cms$uuid, cms$end, cms$stats, cms$qmk)
# Query Row Count
paste0(cms$uri, cms$uuid, cms$end, cms$stats, cms$qmk, cms$query)
# Query Results
paste0(cms$uri, cms$uuid, cms$end, cms$qmk, cms$size, cms$offset, cms$query)

httr2::request() |> 
  httr2::req_perform() |> 
  provider:::parse_string() |> 
  fastplyr::as_tbl() |> 
  head()
```

   - PROVIDER API

```{r}
prov <- list(
  uri = "https://data.cms.gov/provider-data/api/1/datastore/query/<<uuid>>/0?",
  uid = "mj5m-pzi6",
  opt = "schema=false&keys=true&format=json&rowIds=false&count=true&",
  results = "true",
  offset = 0, 
  limit = 10
)

query <- paste0(
  "conditions[0][property]=provider_first_name&",
  "conditions[0][operator]=contains&",
  "conditions[0][value]=JO",
  collapse = "&"
)

httr2::request() |> 
  httr2::req_perform() |> 
  provider:::parse_string() |> 
  fastplyr::as_tbl() |> 
  head()
```
