---
title: "Linking Providers"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Linking Providers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

```{r setup, message=FALSE, warning=FALSE}
library(provider)
library(tidyverse)
library(printr)
```


Exploring links between providers can lead to many interesting insights. For example, there is a hospital in New York named **Elizabethtown Community Hospital**. 

<br>

Looking it up in the **Provider Enrollment** API gives us several avenues to go down:

<br>

```{r}
provider_enrollment(organization_name = "Elizabethtown Community Hospital")
```

```{r echo=FALSE}
e <- provider_enrollment(organization_name = "Elizabethtown Community Hospital")
e_npi <- dplyr::distinct(e, npi)
e_pac <- dplyr::distinct(e, pac_id)
e_enroll <- dplyr::distinct(e, enroll_id)
```


<br>

We can see that it has `r nrow(e_pac)` PAC ID, `r nrow(e_npi)` organizational NPIs, and `r nrow(e_enroll)` Enrollment IDs. Searching for it in the **Hospital Enrollment** API gives us even more detail:

<br>

```{r}
hospital_enrollment(organization_name = "Elizabethtown Community Hospital") |> 
  select(npi, organization_name, pac_id_org, facility_ccn, specialty_code)
```

<br>

The **Hospital Enrollment** API includes only Medicare Part A (hospital) providers, so we only get two rows back, but those include a new data point: two facility CCNs. Plugging those into the **Facility Affiliations** API, we can retrieve information on the individual providers practicing at this hospital. First, the all-numeric CCN (`331302`):

<br>

```{r}
facility_affiliations(facility_ccn = 331302) |> 
  select(-c(middle_name, suffix)) |> 
  head(10)
```
```{r echo=FALSE}
npi <- facility_affiliations(facility_ccn = 331302) |> dplyr::distinct(npi)
npi2 <- facility_affiliations(facility_ccn = "33Z302") |> dplyr::distinct(npi)
```

<br>

That returns `r nrow(npi)` individual providers affiliated with the hospital. Now to search the alphanumeric CCN (`33Z302`):


```{r}
facility_affiliations(facility_ccn = "33Z302")
```

<br>

That returns `r nrow(npi2)` more affiliated individual providers that practice in the Hospital's nursing home, bringing the total to `r nrow(npi) + nrow(npi2)`.

<br>

> An *alphanumeric* CCN represents a sub-unit of the hospital, here a nursing home. We would get the same result if we'd set the `parent_ccn` argument to the numeric CCN, i.e. `facility_affiliations(parent_ccn = 331302)`

<br>

```{r eval=FALSE, echo=FALSE}
unique(elizabethtown$npi) |> 
  map(\(x) nppes_npi(npi = x)) |> 
  list_rbind() |> 
  filter(purpose != "MAILING")
```



