---
title: "Get started with provider"
description: >
  An overview of the basic workflow of provider and the type of data
  it provides access to.
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started with provider}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE, 
  message   = TRUE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%"
)
options(scipen = 999, digits = 2)
library(tibble)
```

```{r}
library(provider)
```

The overarching goal of `{provider}` is to make the experience of accessing
publicly-available Provider data easier and more consistent across a variety of
sources. It aims to accomplish this through the following goals:
   - **Variable Standardization**, for the express purpose of making it easier to understand (and make connections between) each API's output. This will also allow for the removal of duplicate information and greatly simplify the process of merging data across outputs.
   - **Input Validation**. Not only is this simply good practice, it also prevents unnecessary querying of APIs.
   - **Helpful Documentation**. The impetus for this package was to cobble together a motivating example of using a programming language to streamline the process of data acquisition for, among other things, medical coding, billing, and healthcare revenue cycle management. Though it's now grown beyond that, the intended audience remains the same: non-programmers in healthcare who are interested in what a programming language like R can do to make their work easier. As such, the documentation is written with in a way that assumes no prior knowledge of R or programming in general. Domain-specific terminology and concepts are explained in detail, as there is not one person in existence that understands every aspect of the business of health care, including the author of this package.

## Tidy Output
In [**tidy data**](https://tidyr.tidyverse.org/articles/tidy-data.html), every
**column** is a *variable*, every **row** is an *observation*, and every
**cell** is a *single value*.
Many of the outputs of these APIs violate this form by:
   - Storing column headers as values, not variable names
   - Storing multiple variables in one column
To remedy this, there is some post-processing done to the output before it is
returned:

```{r}
order_refer(npi = 1043477615)
```

The `tidy` transformations applied to the output of each function include:
   - Favoring a long format over wide.
   - More descriptive, thematic variable names, involving prefixes and a standardized vocabulary across all outputs
   - Various quality-of-life data transformations (e.g., using `snake_case` for variable names, replacing empty character cells with `NA`; converting years, dates, booleans to their respective data types)
   - Nesting large groups of related columns into lists, to initially emphasize the most important output.

## Provider Identifiers

> **NPI**: A National Provider Identifier (NPI) is a unique 10-digit
identification number issued to health care providers in the United States by
the Centers for Medicare and Medicaid Services (CMS) through the National Plan
and Provider Enumeration System (NPPES). All individual HIPAA–covered healthcare
providers or organizations must obtain an NPI. Once assigned, a provider’s NPI
is permanent and remains with the provider regardless of job or location
changes.

```{r, eval=FALSE}
# Must be 10 digits long
open_payments(year = 2021, npi = 12345691234)

# Must be numeric
nppes(npi = "O12345678912")

# Must pass Luhn check
pending(npi = 001234569123)
```

> **PAC**: A Provider associate-level control ID (PAC ID) is a 10-digit unique
numeric identifier that is assigned to each individual or organization in PECOS.
The PAC ID links all entity-level information (e.g., tax identification numbers
and organizational names) and may be associated with multiple enrollment IDs if
the individual or organization enrolled multiple times under different
circumstances.

```{r, eval=FALSE}
# Must be 10 digits long
affiliations(pac = 0123456789)

# Must be numeric
hospitals(pac_org = "O12345678912")
```

> **ENID**: A Medicare Enrollment ID is a 15-digit unique alphanumeric
identifier that is assigned to each new provider enrollment application. All
enrollment-level information (e.g., enrollment type, enrollment state, provider
specialty and reassignment of benefits) is linked through the Enrollment ID.

```{r, eval=FALSE}
# Must be a character vector
clinicians(enid = 0123456789123456)

# Must be 15 characters long
reassignments(enid = "I123456789123456")

# Must begin with a capital I (Individual) or O (Organization/Group)
providers(enid = "L12345678912345")

# Some functions require one of ID types
hospitals(enid_org = "I20180115000174")
```

> **CCN**: A CMS Certification Number is a standardized sequence of alphanumeric
characters that uniquely identify health care providers and suppliers who
interact with the Medicare and Medicaid programs. Providers and suppliers paid
under Medicare Part A have a 6 digit CCN. Suppliers paid by Part B carriers have
a 10-digit CCN.

> **Taxonomy Code**: A NUCC Healthcare Taxonomy Code is a.

> **Provider Type Code**: A Medicare Provider Type Code is a.

```{r}
provider::provider_type_code
```

