---
title: "Overview of Provider"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview of Provider}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

```{r}
library(provider)
```

<br>

## Example: Opt-Out Provider

<br>

```{r eval=FALSE}
nppes_npi(npi = 1114058443)

order_refer(npi = 1114058443)

opt_out(npi = 1114058443)
```

```{r echo=FALSE}
nppes <- nppes_npi(npi = 1114058443)

nppes_type_npi <- nppes |> 
  dplyr::select(NPI = number, 
                enumeration_type) |> 
  dplyr::mutate(enumeration_type = dplyr::case_when(
    enumeration_type == "NPI-1" ~ "Individual", 
    enumeration_type == "NPI-2" ~ "Organization"))

nppes_basic <- nppes$basic[[1]] |> 
  dplyr::rename_with(~ stringr::str_remove_all(.x, 
                              pattern = "basic_")) |> 
  dplyr::select(name_prefix, 
                first_name, 
                middle_name, 
                last_name, 
                credential, 
                gender, 
                enumeration_date, 
                certification_date, 
                last_updated) |> 
  dplyr::mutate(dplyr::across(dplyr::contains("name"), 
                              stringr::str_to_title))

nppes_tax <- nppes$taxonomies[[1]] |> 
  dplyr::select(code, description = desc, license)

nppes_add1 <- nppes$addresses[[1]] |> 
  dplyr::select(!c(address_purpose, address_1, address_type, country_code, country_name)) |> 
  dplyr::mutate(city = stringr::str_to_title(city),
                state = stringr::str_to_title(campfin::expand_state(state)),
                postal_code = campfin::normal_zip(postal_code),
                telephone_number = campfin::normal_phone(telephone_number),
                fax_number = campfin::normal_phone(fax_number)) |> 
  dplyr::distinct(telephone_number, .keep_all = TRUE)

nppes_add2 <- nppes$addresses[[1]] |> 
  dplyr::select(address_purpose, address_1) |> 
  dplyr::mutate(dplyr::across(dplyr::everything(), stringr::str_to_title)) |> 
  tidyr::pivot_wider(names_from = address_purpose, values_from = address_1, 
                     names_glue = "{address_purpose}_address") |> 
  dplyr::rename_with(tolower)

ord_ref <- order_refer(npi = 1114058443) |> 
  dplyr::select(Refer_to_Part_B = partb, Refer_to_HHAs = hha, Order_DME = dme, Order_PMDs = pmd)

opt <- opt_out(npi = 1114058443) |> 
  dplyr::select(opt_out_effective_date = optout_effective_date, 
                opt_out_end_date = optout_end_date)
  

optex_final <- dplyr::bind_cols(nppes_type_npi, nppes_basic, nppes_add1, nppes_add2, nppes_tax, opt, ord_ref) |> 
  dplyr::mutate(dplyr::across(dplyr::contains("date"), parsedate::parse_date)) |> 
  dplyr::mutate(practice_duration = lubridate::as.duration(lubridate::interval(enumeration_date, lubridate::today())),
                practice_length = as.numeric(practice_duration, "years"),
                opt_out_duration = lubridate::as.duration(lubridate::interval(opt_out_effective_date, opt_out_end_date)),
                opt_out_length = as.numeric(opt_out_duration, "years")) |> 
  dplyr::select(!c(practice_duration, opt_out_duration)) |> 
  dplyr::rename_with(~ stringr::str_replace_all(.x, pattern = "_", replacement = " ")) |>
  dplyr::rename_with(~ stringr::str_to_title(.x)) |> 
  dplyr::rename(NPI = Npi)
``` 


```{r}
optex_final
```

<br>

```{r}
optex_long <- optex_final |> 
  dplyr::mutate(dplyr::across(dplyr::everything(), as.character)) |> 
  tidyr::pivot_longer(cols = dplyr::everything())
```

<br>

```{r}
library(downloadthis)

# CSV file
attach_csv <- optex_long |> 
  downloadthis::download_this(
    output_name = "providercsv",
    output_extension = ".csv",
    button_label = "Download CSV",
    button_type = "default",
    has_icon = TRUE,
    icon = "fa fa-save"
  )
# Excel file
attach_excel <- optex_long |> 
  downloadthis::download_this(
    output_name = "providerxlsx",
    output_extension = ".xlsx",
    button_label = "Download Excel",
    button_type = "primary",
    has_icon = TRUE,
    icon = "fa fa-save"
  )

gt_theme_provider <- function(data,...) {
  data |>
  gt::opt_all_caps() |>
  gt::opt_row_striping() |> 
  gt::opt_table_font(
    font = list(
      gt::google_font("Chivo"),
      gt::default_fonts())) |>
    gt::tab_style(
      style = gt::cell_borders(
        sides = "bottom", 
        color = "transparent", 
        weight = gt::px(2)),
      locations = gt::cells_body(
        columns = TRUE,
        rows = nrow(data$`_data`)))  |> 
  gt::tab_options(
    footnotes.multiline = FALSE,
    row.striping.background_color = "#fafafa",
    table_body.hlines.color = "#f6f7f7",
    table.border.top.width = gt::px(3),
    table.border.top.color = "gray",
    table.border.bottom.color = "gray",
    table.border.bottom.width = gt::px(3),
    column_labels.border.top.width = gt::px(3),
    column_labels.border.top.color = "gray",
    column_labels.border.bottom.width = gt::px(3),
    column_labels.border.bottom.color = "black",
    column_labels.background.color = "white",
    data_row.padding = gt::px(3),
    source_notes.multiline = FALSE,
    source_notes.font.size = 12,
    source_notes.border.bottom.color = "black",
    source_notes.border.bottom.width = gt::px(3),
    table.font.size = 16,
    heading.align = "left",
    ...)
}

add_badge <- function(x){
      add_color <- if (x == "Individual") {
        "background: hsl(116, 60%, 90%); color: hsl(116, 30%, 25%);"
        } else if (x == "Organization") {
          "background: hsl(350, 70%, 90%); color: hsl(350, 45%, 30%);"
        } else if (x != "Individual" | x != "Organization") { x 
          }
      div_out <- htmltools::div(
        style = paste("display: inline-block; padding: 2px 12px; border-radius: 15px; font-weight: 600; font-size: 16px;", add_color), x) 
      as.character(div_out) |> gt::html()
}

add_check_xmark <- function(x) {
  add_checkx <- if (x == TRUE) {
    fontawesome::fa("circle-check", prefer_type = "solid", fill = "green", height = "1.5em", width = "1.5em")
    } else if (x == "FALSE") {
    fontawesome::fa("circle-xmark", prefer_type = "solid", fill = "red")
    } else if (x != "Individual" | x != "Organization") { 
      x 
    }
  div_out <- htmltools::div(style = paste("display: inline-block; padding: 2px 12px; border-radius: 15px; font-weight: 600; font-size: 16px;", add_checkx), x) 
      as.character(div_out) |> gt::html()
  }
```


```{r}
optex_long |> 
  #dplyr::mutate(value = purrr::map(value, add_badge)) |>
  #dplyr::mutate(value = purrr::map(value, add_check_xmark)) |>
  gt::gt() |> 
  gtExtras::gt_add_divider(columns = "name", style = "dotted") |> 
  gt::cols_label(name = "Label", value = "Value") |> 
  gt::tab_row_group(group = "Important Dates", 
                    rows = name %in% c("Enumeration Date", 
                                       "Certification Date", 
                                       "Last Updated", 
                                       "Opt Out Effective Date", 
                                       "Opt Out End Date",
                                       "Practice Length",
                                       "Opt Out Length")) |> 
  gt::tab_row_group(group = "Eligible to Order & Refer", 
                    rows = name %in% c("Refer To Part B", 
                                       "Refer To Hhas", 
                                       "Order Dme", 
                                       "Order Pmds")) |> 
  gt::tab_row_group(group = "Taxonomy", 
                    rows = name %in% c("Code", 
                                       "Description", 
                                       "License")) |> 
  gt::tab_row_group(group = "Address", 
                    rows = name %in% c("Location Address", 
                                       "Mailing Address", 
                                       "City", 
                                       "State", 
                                       "Postal Code", 
                                       "Telephone Number", 
                                       "Fax Number")) |> 
  gt::tab_row_group(group = "Basic Information", 
                    rows = name %in% c("NPI", 
                                       "Enumeration Type", 
                                       "Name Prefix", 
                                       "First Name", 
                                       "Middle Name", 
                                       "Last Name", 
                                       "Credential", 
                                       "Gender")) |> 
  gt::tab_style(style = list(gt::cell_fill(color = "darkred"), gt::cell_text(color = "white", weight = "bold")), locations = gt::cells_row_groups()) |> 
  gt_theme_provider() |> 
  gt::tab_header(title = "Provider Results for NPI 1114058443",
    subtitle = gtExtras::add_text_img("Report generated with", url = "https://raw.githubusercontent.com/andrewallenbruce/provider/main/pkgdown/favicon/apple-touch-icon-180x180.png", height = 25)) |> 
  #gt::fmt_date(columns = c(value), rows = dplyr::contains("date"), date_style = 5) |> 
  #gtExtras::gt_badge(value, palette = c("Individual" = "red")) |> 
  gt::tab_source_note(attach_csv) |> 
  gt::tab_source_note(attach_excel) |> 

  gt::text_transform(locations = gt::cells_body(columns = c(value), 
                     rows = name %in% c("eligible_to_order_and_refer", 
                                       "refer_partb", 
                                       "refer_hha", 
                                       "order_dme", 
                                       "order_pmd")),
                     fn = function(x) {
                       if (x == as.character("TRUE")) {gt::html(fontawesome::fa("circle-check", prefer_type = "solid", fill = "green", height = "1.5em", width = "1.5em"))
                         } else if (x == as.character("FALSE")) {gt::html(fontawesome::fa("circle-xmark", prefer_type = "solid", fill = "red"))
                         }
                     }
                       )
```




<br>

```{r}
provider_enrollment(npi = 1114058443)
```

<br>

## Medicare Order and Referring API

<br>

Is the provider currently eligible to make referrals to Medicare Part B or a Home Health Agency (HHA)? Order Durable Medical Equipment (DME) or Power Mobility Devices (PMDs)? Search Medicare's **Order and Referring API** with `provider_moar()`:

<br>

```{r}
order_refer(npi = 1114058443)
```

<br>

## Medicare Provider and Supplier Taxonomy Crosswalk API

<br>

You may need to find Medicare's specialty codes for this provider's taxonomies. Using the output from the NPPES search in the first example, you can search Medicare's **Provider and Supplier Taxonomy Crosswalk API** with `provider_mpstc()`:

<br>

```{r}
taxonomy_crosswalk(taxonomy_code = "2084P0800X")
```

<br>

```{r}
revalidation_date(npi = 1114058443)
```

<br>

Providers may need to update their digital contact information in the NPPES system. To check, you can access the **CMS Public Reporting of Missing Digital Contact Information API** with `provider_promdci()`. If they appear in the search results, it's time to update their NPPES contact information:

<br>

```{r}
missing_information(npi = 1114058443)
```

<br>

```{r}
opt_out(npi = 1114058443)
```

<br>

Using `provider_mpop()`, you can access **Medicare's Physician & Other Practitioners - by Provider and Service API**:

<br>

```{r}
physician_by_service(npi = 1114058443, year = "2020")
```


<br>

This API contains data going back to 2013, so you can perform a long-term analysis of a provider's Medicare data:

<br>

```{r}
purrr::map_dfr(as.character(2013:2020), ~physician_by_service(npi = 1114058443, year = .x)) |> 
  dplyr::group_by(hcpcs_cd, hcpcs_desc) |> 
  dplyr::summarise(
    Benefits = sum(tot_benes),
    Services = sum(tot_srvcs),
    Avg_Billed = janitor::round_half_up(mean(avg_sbmtd_chrg), digits = 2),
    Avg_Allowed = janitor::round_half_up(mean(avg_mdcr_alowd_amt), digits = 2),
    Avg_Payment = janitor::round_half_up(mean(avg_mdcr_pymt_amt), digits = 2)) |> 
  dplyr::ungroup() |> 
  dplyr::rename(HCPCS = hcpcs_cd, 
                "HCPCS Description" = hcpcs_desc,
                "Avg Charge" = Avg_Billed,
                "Avg Allowed" = Avg_Allowed,
                "Avg Payment" = Avg_Payment) |> 
  dplyr::arrange(dplyr::desc(Services)) |> 
  knitr::kable()
```



Using packages like {gt} & {ggplot2}, you can create tables and graphs for reporting purposes:

<br>

<details>

<summary>Click for Table Code</summary>


```{r echo=FALSE, eval=FALSE, include=FALSE}
# First row of data
mpop_ex_2020_row1 <- mpop_ex_2020 |> dplyr::filter(dplyr::row_number() %in% 1)

# First, last, credentials
mpop_ex_name_cred <- stringr::str_c(
  stringr::str_trim(mpop_ex_2020_row1$rndrng_prvdr_first_name, "both"), " ",
  stringr::str_trim(mpop_ex_2020_row1$rndrng_prvdr_last_org_name, "both"), ", ",
  stringr::str_trim(mpop_ex_2020_row1$rndrng_prvdr_crdntls, "both"))

# NPI
mpop_ex_npi <- stringr::str_c(stringr::str_trim(mpop_ex_2020_row1$rndrng_npi, "both"), "")

# Address
mpop_ex_address <- stringr::str_c(
  stringr::str_trim(mpop_ex_2020_row1$rndrng_prvdr_st1, "both"), " ",
  stringr::str_trim(mpop_ex_2020_row1$rndrng_prvdr_city, "both"), ", ",
  stringr::str_trim(mpop_ex_2020_row1$rndrng_prvdr_state_abrvtn, "both"), " ",
  stringr::str_trim(mpop_ex_2020_row1$rndrng_prvdr_zip5, "both"))



gt_table <- mpop_13_20 |>
  dplyr::select(year,
                hcpcs     = hcpcs_cd,
                benefits  = tot_benes,
                services  = tot_srvcs,
                avg_bill  = avg_sbmtd_chrg,
                avg_allow = avg_mdcr_alowd_amt,
                avg_pay   = avg_mdcr_pymt_amt) |> 
  dplyr::group_by(hcpcs) |> 
  dplyr::summarize(
    ben_sum    = sum(benefits),
    ben_mean   = mean(benefits),
    ben_spark  = list(benefits),
    serv_sum   = sum(services),
    serv_mean  = mean(services),
    serv_spark = list(services),
    char_sum   = sum(avg_bill),
    char_mean  = mean(avg_bill),
    char_spark = list(avg_bill),
    all_sum    = sum(avg_allow),
    all_mean   = mean(avg_allow),
    all_spark  = list(avg_allow),
    pay_sum    = sum(avg_pay),
    pay_mean   = mean(avg_pay),
    pay_spark  = list(avg_pay),
    .groups = "drop") |> 
  dplyr::filter(ben_sum > 22) |> 
  dplyr::arrange(desc(ben_sum))


gt_output <- gt_table |> 
  gt::gt() |> 
  gt::tab_header(
  title = gt::md(paste0(mpop_ex_name_cred, "**Medicare Data Report**: 2013 - 2020.")), 
  subtitle = gt::md(
  "NPI: 1760485387. HCPCS Codes with a beneficiary count *less than 30* have been excluded.")) |> 
  gtExtras::gt_theme_538() |> 
  gt::tab_options(footnotes.multiline = TRUE, 
                  table.font.size = "16px",
                  heading.title.font.size = "22px") |> 
  gtExtras::gt_plt_sparkline(ben_spark, 
                             type = "ref_iqr", 
                             fig_dim = c(5, 30), 
                             same_limit = FALSE, 
                             label = FALSE,
                             palette = c("black", 
                                         "black", 
                                         "blue", 
                                         "green", 
                                         "blue")) |> 
  gtExtras::gt_plt_sparkline(serv_spark, 
                             type = "ref_iqr", 
                             fig_dim = c(5, 30), 
                             same_limit = FALSE, 
                             label = FALSE,
                             palette = c("black", 
                                         "black", 
                                         "blue", 
                                         "green", 
                                         "blue")) |> 
  gtExtras::gt_plt_sparkline(char_spark, 
                             type = "ref_iqr", 
                             fig_dim = c(5, 30), 
                             same_limit = FALSE, 
                             label = FALSE,
                             palette = c("black", 
                                         "black", 
                                         "blue", 
                                         "green", 
                                         "orange")) |> 
  gtExtras::gt_plt_sparkline(all_spark, 
                             type = "ref_iqr", 
                             fig_dim = c(5, 30), 
                             same_limit = FALSE, 
                             label = FALSE,
                             palette = c("black", 
                                         "black", 
                                         "blue", 
                                         "green", 
                                         "orange")) |> 
  gtExtras::gt_plt_sparkline(pay_spark, 
                             type = "ref_iqr", 
                             fig_dim = c(5, 30), 
                             same_limit = FALSE, 
                             label = FALSE,
                             palette = c("black", 
                                         "black", 
                                         "blue", 
                                         "green", 
                                         "orange")) |> 
  gtExtras::gt_add_divider(columns = "hcpcs", 
                           style = "solid", 
                           include_labels = FALSE,
                           weight = gt::px(3),
                           color = "gray") |>
  gt::fmt_number(columns = c(ben_sum:ben_mean, 
                             serv_sum:serv_mean), 
                             decimals = 0) |> 
  gt::fmt_currency(columns = c(char_sum:char_mean, 
                               all_sum:all_mean, 
                               pay_sum:pay_mean), 
                               currency = "USD") |> 
  gt::tab_spanner(label = "Beneficiaries", 
                  id = "ben", 
                  columns = c(ben_sum, 
                              ben_mean, 
                              ben_spark)) |> 
  gt::tab_spanner(label = "Services", 
                  id = "serv", 
                  columns = c(serv_sum, 
                              serv_mean, 
                              serv_spark)) |> 
  gt::tab_spanner(label = "Submitted Charge", 
                  columns = c(char_sum,
                              char_mean, 
                              char_spark)) |> 
  gt::tab_spanner(label = "Allowed Amount", 
                  columns = c(all_sum,
                              all_mean, 
                              all_spark)) |> 
  gt::tab_spanner(label = "Payment", 
                  columns = c(pay_sum,
                              pay_mean, 
                              pay_spark)) |> 
  gt::cols_label(ben_sum = "Count", 
                 ben_mean = "Average", 
                 ben_spark = "Trend") |> 
  gt::cols_label(serv_sum = "Count", 
                 serv_mean = "Average", 
                 serv_spark = "Trend") |> 
  gt::cols_label(char_sum = "Sum",
                 char_mean = "Average", 
                 char_spark = "Trend") |> 
  gt::cols_label(all_sum = "Sum",
                 all_mean = "Average", 
                 all_spark = "Trend") |> 
  gt::cols_label(pay_sum = "Sum", 
                 pay_mean = "Average", 
                 pay_spark = "Trend") |> 
  gt::tab_source_note(
    source_note = gt::md("Data Source: **Medicare** Physician & Other Practitioners by Provider and Service, 2013 - 2020.")) |> 
  gt::tab_footnote(
    footnote = gt::md("Number of *distinct* Medicare beneficiaries receiving the service for each HCPCS code."), 
    locations = gt::cells_column_spanners(spanners = "ben")) |> 
  gt::tab_footnote(
    footnote = gt::md("Number of services provided. *Note: The metrics used to count the number provided can vary from service to service.*"),
    locations = gt::cells_column_spanners(spanners = "serv")) |> 
  gtExtras::gt_color_rows(columns = ben_sum, 
                          palette = "RColorBrewer::Blues", pal_type = "continuous", domain = range(gt_table$ben_sum)) |> 
  gtExtras::gt_color_rows(columns = ben_mean, 
                          palette = "RColorBrewer::Blues", pal_type = "continuous", domain = range(gt_table$ben_mean)) |> 
  gtExtras::gt_color_rows(columns = serv_sum, 
                          palette = "RColorBrewer::Blues", pal_type = "continuous", domain = range(gt_table$serv_sum)) |> 
  gtExtras::gt_color_rows(columns = serv_mean, 
                          palette = "RColorBrewer::Blues", pal_type = "continuous", domain = range(gt_table$serv_mean)) |> 
  gtExtras::gt_color_rows(columns = char_sum, 
                          palette = "RColorBrewer::Oranges", pal_type = "continuous", domain = range(gt_table$char_sum)) |> 
  gtExtras::gt_color_rows(columns = char_mean, 
                          palette = "RColorBrewer::Oranges", pal_type = "continuous", domain = range(gt_table$char_mean)) |> 
  gtExtras::gt_color_rows(columns = all_sum, 
                          palette = "RColorBrewer::Oranges", pal_type = "continuous", domain = range(gt_table$all_sum)) |> 
  gtExtras::gt_color_rows(columns = all_mean, 
                          palette = "RColorBrewer::Oranges", pal_type = "continuous", domain = range(gt_table$all_mean)) |> 
  gtExtras::gt_color_rows(columns = pay_sum, 
                          palette = "RColorBrewer::Oranges", pal_type = "continuous", domain = range(gt_table$pay_sum)) |> 
  gtExtras::gt_color_rows(columns = pay_mean, 
                          palette = "RColorBrewer::Oranges", pal_type = "continuous", domain = range(gt_table$pay_mean)) |> 
  gt::opt_vertical_padding(scale = 1.5)

#gt::gtsave(gt_output, filename = "gt_provider3.png", expand = 20, zoom = 2, vwidth = 1500)
```

</details>

<br>
<br>
