---
title: "Beneficiary Enrollment"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
options(scipen = 999)
```

```{r}
library(provider)
```

> The **Medicare Monthly Enrollment** dataset provides current monthly information on the number of Medicare beneficiaries with hospital/medical/prescription drug coverage, available for several geographic areas including national, state/territory, and county. The data can be further broken down by health care delivery (e.g. *Original Medicare* vs. *Medicare Advantage*) and includes enrollee counts on a rolling 12-month basis, providing information on yearly trends as well.

## Search Examples

The `level` argument has three options: `National`, `State`, and `County`. 

Setting it to `National` will return yearly and monthly national totals:

```{r}
beneficiary_enrollment(level = "National") |> head(10)
```

Setting `level` to `National` and the `period` argument to `Year` will return yearly national totals only:

```{r}
beneficiary_enrollment(level = "National", 
                       period = "Year") |> 
  head(10)
```

Setting `level` to `State` and `period` to `Year` will return yearly totals for each state:

```{r}
beneficiary_enrollment(level = "State", 
                       period = "Year") |> 
  head(10)
```



```{r}
beneficiary_enrollment(level = "State", 
                       period = "Month") |> 
  head(10)
```


### `state` & `county`

Select a particular state:

```{r}
beneficiary_enrollment(period = "Year", 
                       level = "State", 
                       state = "GA") |> 
  head(10)
```


Each county in that state:

```{r}
beneficiary_enrollment(period = "Year", 
                       level = "County", 
                       state_name = "Georgia") |> 
  head(10)
```

Or a particular county:

```{r}
beneficiary_enrollment(period = "Year", 
                       level = "County", 
                       state = "GA", 
                       county = "Lowndes") |> 
  head(10)
```

<br><br>

## Visualizations

<details><summary>Code for plots</summary>

```{r}
national <- beneficiary_enrollment(period = "Year", level = "National") |> 
  dplyr::select(year, level, bene_total, bene_orig, bene_ma_oth) |> 
  dplyr::mutate(pct_orig = bene_orig / bene_total,
                pct_ma = bene_ma_oth / bene_total) |> 
  provider:::change_abs(bene_total, year) |> 
  provider:::change_pct(bene_total, bene_total_chg, year) |> 
  dplyr::select(year, level, dplyr::contains("pct"))

state <- beneficiary_enrollment(period = "Year", level = "State", state = "GA") |> 
  dplyr::select(year, level, bene_total, bene_orig, bene_ma_oth) |> 
  dplyr::mutate(pct_orig = bene_orig / bene_total,
                pct_ma = bene_ma_oth / bene_total) |> 
  provider:::change_abs(bene_total, year) |> 
  provider:::change_pct(bene_total, bene_total_chg, year) |> 
  dplyr::select(year, level, dplyr::contains("pct"))

county <- beneficiary_enrollment(period = "Year", level = "County", state = "GA", county = "Lowndes") |> 
  dplyr::select(year, level, bene_total, bene_orig, bene_ma_oth) |> 
  dplyr::mutate(pct_orig = bene_orig / bene_total,
                pct_ma = bene_ma_oth / bene_total) |> 
  provider:::change_abs(bene_total, year) |> 
  provider:::change_pct(bene_total, bene_total_chg, year) |> 
  dplyr::select(year, level, dplyr::contains("pct"))

enrollment <- dplyr::bind_rows(national, state, county)

### PLOTS

total <- enrollment |> 
  dplyr::select(year, level, bene_total_pct) |> 
  dplyr::filter(!is.na(bene_total_pct)) |> 
  ggplot2::ggplot(ggplot2::aes(group = level, 
                               fill = level, 
                               color = level)) +
  ggplot2::geom_point(ggplot2::aes(year, bene_total_pct)) +
  ggplot2::geom_line(ggplot2::aes(year, bene_total_pct)) +
  ggplot2::scale_y_continuous(labels = scales::label_percent()) +
  gghighlight::gghighlight(max(bene_total_pct) > 0, 
                           line_label_type = "sec_axis", 
                           label_key = level) +
  ggplot2::theme(axis.text.y.right = ggplot2::element_text(size = 10)) +
  ggplot2::scale_x_continuous(n.breaks = 9) +
  #himni::gg_theme() +
  #ggplot2::ggtitle("Yearly Percentage Change of Total Medicare Beneficiaries") +
  #ggplot2::facet_wrap(~level, ncol = 1) +
  ggplot2::xlab(label = NULL) + 
  ggplot2::ylab(label = NULL)

orig <- enrollment |> 
  ggplot2::ggplot(ggplot2::aes(group = level, 
                               fill = level, 
                               color = level)) +
  ggplot2::geom_point(ggplot2::aes(year, pct_orig), shape = 21, colour = "black", fill = "white", size = 1, stroke = 0.5) +
  ggplot2::geom_line(ggplot2::aes(year, pct_orig)) +
  #ggplot2::scale_y_reverse() +
  ggplot2::scale_y_continuous(labels = scales::label_percent()) +
  gghighlight::gghighlight(max(pct_orig) > 0, 
                           line_label_type = "sec_axis", 
                           label_key = level) +
  ggplot2::theme(axis.text.y.right = ggplot2::element_text(size = 10)) +
  ggplot2::scale_x_continuous(n.breaks = 10) +
  ggplot2::coord_flip() +
  #himni::gg_theme() +
  #ggplot2::ggtitle("Percentage of Medicare Beneficiaries with Original Medicare") +
  ggplot2::xlab(label = NULL) + 
  ggplot2::ylab(label = NULL)

ma <- enrollment |> 
  ggplot2::ggplot(ggplot2::aes(group = level, 
                               fill = level, 
                               color = level)) +
  ggplot2::geom_point(ggplot2::aes(year, pct_ma), shape = 21, colour = "black", fill = "white", size = 1, stroke = 0.5) +
  ggplot2::geom_line(ggplot2::aes(year, pct_ma)) +
  ggplot2::scale_y_continuous(labels = scales::label_percent()) +
  gghighlight::gghighlight(max(pct_ma) > 0, 
                           line_label_type = "sec_axis", 
                           label_key = level) +
  ggplot2::theme(axis.text.y.right = ggplot2::element_text(size = 10)) +
  ggplot2::scale_x_continuous(n.breaks = 10) +
  ggplot2::coord_flip() +
  #himni::gg_theme() +
  #ggplot2::ggtitle("Percentage of Medicare Beneficiaries with Medicare Advantage") +
  ggplot2::xlab(label = NULL) + 
  ggplot2::ylab(label = NULL)
```


</details>


```{r, fig.height=7}
library(patchwork)
patchwork <- total / (orig + ma)
patchwork + 
  ggplot2::theme_minimal()
```

<br>

<details><summary>Code for tables</summary>

```{r}
national <- beneficiary_enrollment(period = "Year", level = "National")

national_bars <- national |> 
  dplyr::select(year, bene_orig, bene_ma_oth) |> 
  dplyr::mutate(pct_orig = bene_orig / (bene_orig + bene_ma_oth),
                pct_ma = bene_ma_oth / (bene_orig + bene_ma_oth)) |> 
  tidyr::pivot_longer(cols = c(pct_orig, pct_ma), 
                      names_to = "measure", 
                      values_to = "pct") |> 
  dplyr::group_by(year) |> 
  dplyr::summarise(list_data = list(pct), .groups = "drop")

national_base <- national |> 
  dplyr::select(year, bene_total) |> 
  provider:::change_abs(bene_total, year) |> 
  provider:::change_pct(bene_total, bene_total_chg, year)

national <- dplyr::left_join(national_bars, national_base, 
                             by = dplyr::join_by(year)) |> 
  dplyr::relocate(list_data, .after = bene_total_pct)

national_gt <- national |>
  provider:::gt_prov(divider = c("year", "bene_total_chg"),
                     title = gt::md("**National** Medicare Beneficiary Enrollment: **2013 - 2022**"),
                     subtitle = gt::md("National Totals, Year-Over-Year"),
                     source = gt::md("Source: [Medicare Monthly Enrollment API](https://data.cms.gov/summary-statistics-on-beneficiary-enrollment/medicare-and-medicaid-reports/medicare-monthly-enrollment)")) |> 
  gt::tab_style(
    style = gt::cell_text(font = c(gt::google_font(name = "Fira Code"), 
                                   gt::default_fonts())),
    locations = gt::cells_body(columns = c(bene_total, 
                                           bene_total_chg))) |> 
  gt::fmt_number(bene_total, suffixing = TRUE, decimals = 2) |> 
  gt::fmt_number(bene_total_chg, suffixing = TRUE, force_sign = TRUE, decimals = 1) |> 
  gt::fmt_percent(columns = bene_total_pct, decimals = 1, force_sign = TRUE) |> 
  gt::cols_merge_n_pct(col_n = bene_total_chg,
                       col_pct = bene_total_pct) |>
  gt::cols_label(bene_total = "Total",
                 bene_total_chg = gt::md("Change (%)")) |> 
  gtExtras::gt_plt_bar_stack(
    column = list_data, 
    width = 80,
    labels = c("Original  ", " Advantage"),
    palette = c("#ff4343", "black"),
    fmt_fn = scales::label_percent(accuracy = 0.1, suffix = " %"))
```


</details>

```{r, echo=FALSE, eval=TRUE}
national_gt
```


<br>

<details><summary>Code for table</summary>

```{r}
state <- beneficiary_enrollment(period = "Year", level = "State", state = "GA")

state_bars <- state |> 
  dplyr::select(year, bene_orig, bene_ma_oth) |> 
  dplyr::mutate(pct_orig = bene_orig / (bene_orig + bene_ma_oth),
                pct_ma = bene_ma_oth / (bene_orig + bene_ma_oth)) |> 
  tidyr::pivot_longer(cols = c(pct_orig, pct_ma), 
                      names_to = "measure", 
                      values_to = "pct") |> 
  dplyr::group_by(year) |> 
  dplyr::summarise(list_data = list(pct), .groups = "drop")

state_base <- state |> 
  dplyr::select(year, bene_total) |> 
  provider:::change_abs(bene_total, year) |> 
  provider:::change_pct(bene_total, bene_total_chg, year)

state <- dplyr::left_join(state_bars, state_base, 
                          by = dplyr::join_by(year)) |> 
  dplyr::relocate(list_data, .after = bene_total_pct)

state_gt <- state |>
  provider:::gt_prov(divider = c("year", "bene_total_chg"),
                     title = gt::md("**Georgia** Medicare Beneficiary Enrollment: **2013 - 2022**"),
                     subtitle = gt::md("State Totals, Year-Over-Year"),
                     source = gt::md("Source: [Medicare Monthly Enrollment API](https://data.cms.gov/summary-statistics-on-beneficiary-enrollment/medicare-and-medicaid-reports/medicare-monthly-enrollment)")) |> 
  gt::tab_style(
    style = gt::cell_text(font = c(gt::google_font(name = "Fira Code"), 
                                   gt::default_fonts())),
    locations = gt::cells_body(columns = c(bene_total, 
                                           bene_total_chg))) |> 
  gt::fmt_number(bene_total, suffixing = TRUE, decimals = 2) |> 
  gt::fmt_number(bene_total_chg, suffixing = TRUE, force_sign = TRUE, decimals = 1) |> 
  gt::fmt_percent(columns = bene_total_pct, decimals = 1, force_sign = TRUE) |> 
  gt::cols_merge_n_pct(col_n = bene_total_chg,
                       col_pct = bene_total_pct) |>
  gt::cols_label(bene_total = "Total",
                 bene_total_chg = gt::md("Change (%)")) |> 
  gtExtras::gt_plt_bar_stack(
    column = list_data, 
    width = 80,
    labels = c("Original  ", " Advantage"),
    palette = c("#ff4343", "black"),
    fmt_fn = scales::label_percent(accuracy = 0.1, suffix = " %"))
```


</details>

```{r, echo=FALSE, eval=TRUE}
state_gt
```


<br>

<details><summary>Code for table</summary>

```{r}
county <- beneficiary_enrollment(period = "Year", level = "County", state = "GA", county = "Lowndes")

county_bars <- county |> 
  dplyr::select(year, bene_orig, bene_ma_oth) |> 
  dplyr::mutate(pct_orig = bene_orig / (bene_orig + bene_ma_oth),
                pct_ma = bene_ma_oth / (bene_orig + bene_ma_oth)) |> 
  tidyr::pivot_longer(cols = c(pct_orig, pct_ma), 
                      names_to = "measure", 
                      values_to = "pct") |> 
  dplyr::group_by(year) |> 
  dplyr::summarise(list_data = list(pct), .groups = "drop")

county_base <- county |> 
  dplyr::select(year, bene_total) |> 
  provider:::change_abs(bene_total, year) |> 
  provider:::change_pct(bene_total, bene_total_chg, year)

county <- dplyr::left_join(county_bars, county_base, 
                          by = dplyr::join_by(year)) |> 
  dplyr::relocate(list_data, .after = bene_total_pct)

county_gt <- county |>
  provider:::gt_prov(divider = c("year", "bene_total_chg"),
                     title = gt::md("**Lowndes County, Georgia** Medicare Beneficiary Enrollment: **2013 - 2022**"),
                     subtitle = gt::md("County Totals, Year-Over-Year"),
                     source = gt::md("Source: [Medicare Monthly Enrollment API](https://data.cms.gov/summary-statistics-on-beneficiary-enrollment/medicare-and-medicaid-reports/medicare-monthly-enrollment)")) |> 
  gt::tab_style(
    style = gt::cell_text(font = c(gt::google_font(name = "Fira Code"), 
                                   gt::default_fonts())),
    locations = gt::cells_body(columns = c(bene_total, 
                                           bene_total_chg))) |> 
  gt::fmt_number(bene_total, suffixing = TRUE, decimals = 2) |> 
  gt::fmt_number(bene_total_chg, suffixing = TRUE, force_sign = TRUE, decimals = 1) |> 
  gt::fmt_percent(columns = bene_total_pct, decimals = 1, force_sign = TRUE) |> 
  gt::cols_merge_n_pct(col_n = bene_total_chg,
                       col_pct = bene_total_pct) |>
  gt::cols_label(bene_total = "Total",
                 bene_total_chg = gt::md("Change (%)")) |> 
  gtExtras::gt_plt_bar_stack(
    column = list_data, 
    width = 80,
    labels = c("Original  ", " Advantage"),
    palette = c("#ff4343", "black"),
    fmt_fn = scales::label_percent(accuracy = 0.1, suffix = " %"))
```


</details>

```{r, echo=FALSE, eval=TRUE}
county_gt
```


<br>

<details><summary>Code for table</summary>

```{r}
# National by Year
tot_nation <- beneficiary_enrollment(level = "National", 
                                     period = "Year") |>
  dplyr::select(year, 
                level, 
                total = bene_total,
                orig = bene_orig,
                ma = bene_ma_oth,
                aged = bene_aged_total, 
                disabled = bene_dsb_total, 
                partsAB = bene_ab_total, 
                partD = bene_rx_total)
# State by Year
tot_state <- beneficiary_enrollment(level = "State", 
                                    period = "Year", 
                                    state = "GA") |> 
  dplyr::select(year, 
                state_name, 
                total = bene_total, 
                orig = bene_orig,
                ma = bene_ma_oth,
                aged = bene_aged_total, 
                disabled = bene_dsb_total, 
                partsAB = bene_ab_total, 
                partD = bene_rx_total) |> 
  dplyr::rename(level = state_name)
# County by Year
tot_county <- beneficiary_enrollment(level = "County", 
                                     period = "Year", 
                                     state = "GA", 
                                     county = "Lowndes") |> 
  dplyr::select(year, 
                county, 
                total = bene_total,
                orig = bene_orig,
                ma = bene_ma_oth,
                aged = bene_aged_total, 
                disabled = bene_dsb_total, 
                partsAB = bene_ab_total, 
                partD = bene_rx_total) |> 
  dplyr::rename(level = county)
# Bind together, calculate stats
final <- dplyr::bind_rows(tot_nation, tot_state, tot_county) |> 
  dplyr::group_by(level) |> 
  provider:::change_abs(total, year) |> 
  provider:::change_pct(total, total_chg, year) |> 
  dplyr::ungroup() |> 
  dplyr::mutate(orig_pct = orig / total,
                ma_pct = ma / total,
                aged_pct = aged / total,
                disabled_pct = disabled / total,
                ab_pct = partsAB / total,
                d_pct = partD / total) |> 
  dplyr::select(year, 
                level, 
                total_pct_chg = total_pct, 
                orig_pct,
                ma_pct,
                aged_pct, 
                disabled_pct, 
                ab_pct, 
                d_pct)
## gt Table
gt_pct <- final |>   
  gt::gt() |> 
  gt::tab_style(style = gt::cell_text(
    font = c(gt::google_font(name = "Fira Code"), gt::default_fonts())),
    locations = gt::cells_body(columns = dplyr::contains("pct"))) |> 
  gtExtras::gt_theme_538() |> 
  gt::fmt_percent(columns = dplyr::contains("pct"), decimals = 1) |> 
  gt::fmt_percent(columns = c(total_pct_chg), decimals = 1, force_sign = TRUE) |> 
  gt::sub_missing(columns = dplyr::everything(), missing_text = "--") |> 
  gt::cols_label(total_pct_chg = "% Change",
                 orig_pct = "Original",
                 ma_pct = "MA",
                 aged_pct = "Aged",
                 disabled_pct = "Disabled", 
                 ab_pct = "Pts A & B",
                 d_pct = "Part D") |> 
  gtExtras::gt_add_divider(
    columns = c("level", 
                "total_pct_chg", 
                "ma_pct", 
                "disabled_pct"), 
    style = "solid",
    color = "black",
    weight = gt::px(3),
    include_labels = FALSE) |>
  gt::tab_header(
    title = gt::md("Medicare Beneficiaries: **2013 - 2022**"),
    subtitle = gt::md("National, State, & County Percentage Comparisons for **Valdosta, Georgia**")) |> 
  gt::tab_source_note(source_note = "Source: data.cms.gov")
#|> gt::opt_table_font(font = gt::google_font(name = "Karla"))
```

</details>

```{r, echo=FALSE, eval=TRUE}
gt_pct
```

<br>



<details><summary>Code for table</summary>

```{r}
gt_comp <- beneficiary_enrollment(level = "National", 
                                  period = "Year") |> 
  dplyr::select(!c(period:fips)) |> 
  tidyr::pivot_longer(cols = dplyr::starts_with("bene_"), 
                      names_to = "stat", 
                      values_to = "value") |> 
  tidyr::pivot_wider(names_from = year, 
                     values_from = value) |> 
  gt::gt(rowname_col = "stat") |> 
  gt::tab_style(
    style = gt::cell_text(font = c(gt::google_font(name = "Fira Code"), 
                                   gt::default_fonts())),
    locations = gt::cells_body(columns = c(2:11))) |> 
  gtExtras::gt_theme_538() |> 
  gt::fmt_number(columns = c(2:11), suffixing = TRUE, decimals = 1) |> 
  gt::tab_row_group(label = gt::md("**Disabled Beneficiaries**"), 
                    rows = c("bene_dsb_total", 
                             "bene_dsb_no_esrd", 
                             "bene_dsb_esrd")) |> 
  gt::tab_row_group(label = gt::md("**Aged Beneficiaries**"), 
                    rows = c("bene_aged_total", 
                             "bene_aged_no_esrd", 
                             "bene_aged_esrd")) |> 
  gt::tab_row_group(label = gt::md("**Medicare Part D**"), 
                    rows = c("bene_rx_total", 
                             "bene_rx_pdp", 
                             "bene_rx_mapd", 
                             "bene_rx_elig", 
                             "bene_rx_full", 
                             "bene_rx_part", 
                             "bene_rx_none")) |> 
  gt::tab_row_group(label = gt::md("**Medicare Parts A & B**"), 
                    rows = c("bene_ab_total", 
                             "bene_ab_orig", 
                             "bene_ab_ma_oth")) |> 
  gt::tab_row_group(label = gt::md("**Original Medicare** / **Medicare Advantage**"), 
                    rows = c("bene_orig", 
                             "bene_ma_oth")) |> 
  gt::tab_row_group(label = gt::md("**Total Beneficiaries**"), 
                    rows = c("bene_total")) |> 
  gt::tab_header(title = gt::md(
    "Medicare Beneficiary Enrollment: **2013 - 2022**"),
    subtitle = gt::md("National Totals, Month-Over-Month")) |> 
  gt::tab_source_note(source_note = "Source: data.cms.gov")
```

</details>

```{r, echo=FALSE, eval=TRUE}
gt_comp
```


```{r, echo=FALSE, include=FALSE, eval=FALSE}
mon_nat_list <- national |> 
  dplyr::filter(period %in% month.name) |> 
  dplyr::select(year, period, bene_orig, bene_ma_oth) |> 
  dplyr::mutate(pct_orig = bene_orig / (bene_orig + bene_ma_oth),
                pct_ma = bene_ma_oth / (bene_orig + bene_ma_oth)) |> 
  tidyr::pivot_longer(cols = c(pct_orig, pct_ma), 
                      names_to = "measure", 
                      values_to = "pct") |> 
  dplyr::group_by(year, period) |> 
  dplyr::summarise(list_data = list(pct), .groups = "drop")

mon_nat_base <- national |> 
  dplyr::filter(period %in% month.name) |> 
  dplyr::select(year, period, bene_total) |> 
  provider:::change_abs(bene_total, year) |> 
  provider:::change_pct(bene_total, bene_total_chg, year)

mon <- dplyr::left_join(mon_nat_base, mon_nat_list, 
                 by = dplyr::join_by(year, period))

mon |> 
  gt::gt() |> 
  gt::tab_style(
    style = gt::cell_text(font = c(gt::google_font(name = "Fira Code"), 
                                   gt::default_fonts())),
    locations = gt::cells_body(columns = c(bene_total, bene_total_chg))) |> 
  gt::fmt_number(bene_total, suffixing = TRUE, decimals = 2) |> 
  gt::fmt_number(bene_total_chg, suffixing = TRUE, force_sign = TRUE, decimals = 1) |> 
  gt::fmt_percent(columns = bene_total_pct, decimals = 1, force_sign = TRUE) |> 
  gt::sub_missing(columns = dplyr::everything(), missing_text = "--") |> 
  gt::cols_merge_n_pct(col_n = bene_total_chg, 
                       col_pct = bene_total_pct) |> 
  gt::cols_align(align = "right", 
                 columns = period) |> 
  gt::cols_label(period = "Month", 
                 bene_total = "Total", 
                 bene_total_chg = gt::md("Change (%)")) |> 
  gtExtras::gt_add_divider(columns = c("period", 
                                       "bene_total_chg"), 
                           style = "solid",
                           color = "black",
                           weight = gt::px(2),
                           include_labels = FALSE) |> 
  gtExtras::gt_plt_bar_stack(column = list_data,
                             width = 40,
                             labels = c("Original  ", "  Advantage"),
                             palette = c("#ff4343", "black"),
                             fmt_fn = scales::label_percent(suffix = " %")) |> 
  gt::tab_header(title = gt::md(
    "Medicare Beneficiary Enrollment: **2013 - 2022**"),
    subtitle = gt::md("National Totals, Month-Over-Month")) |> 
  gt::tab_source_note(source_note = "Source: data.cms.gov") |>
  gtExtras::gt_theme_538()
```


## Data Dictionary

```{r}
beneficiary_enrollment(period = "Year", 
                       level = "State",
                       state = "GA") |> names()
```

```{r echo=FALSE}
tibble::tribble(
  ~Description,                                                   ~Variable,         ~Definition,
  "Year",                                                          "`year`",          "Indicates the calendar year of Medicare enrollment",
  "Month",                                                         "`month`",           "Indicates the month of Medicare enrollment",
  "Beneficiary State",                                             "`state`",       "Area of beneficiary residence",
  "Beneficiary County",                                            "`county`",                    "County of beneficiary residence",
  "Total Beneficiaries",                                           "`bene_total`",                      "Count of all Medicare beneficiaries",
  "Original Medicare Beneficiaries",                               "`bene_orig`",               "Count of all Original Medicare beneficiaries",
  "Medicare Advantage and Other Health Plan Beneficiaries",         "`bene_ma_oth`",       "Count of all Medicare Advantage and Other Health Plan beneficiaries",
  "Total Aged Beneficiaries",                                       "`bene_aged_total`",         "Count of Medicare aged beneficiaries",
  "Aged ESRD Beneficiaries",                                        "`bene_aged_esrd`",        "Count of Medicare aged beneficiaries with End Stage Renal Disease",
  "Aged Beneficiaries Without ESRD",                                "`bene_aged_no_esrd`",     "Count of Medicare aged beneficiaries without End Stage Renal Disease",
  "Total Disabled Beneficiaries",                                   "`bene_dsb_total`",               "Count of Medicare disabled beneficiaries",
  "Disabled Beneficiaries with ESRD and ESRD Only Beneficiaries",  "`bene_dsb_esrd`", "Count of Medicare disabled beneficiaries with End Stage Renal Disease and beneficiaries with End Stage Renal Disease only", 
  "Disabled Beneficiaries Without ESRD",                          "`bene_no_esrd`", "Count of Medicare disabled beneficiaries without End Stage Renal Disease",
  "Total Medicare Part A and Part B Beneficiaries",               "`bene_ab_total`", "Count of Medicare beneficiaries enrolled in Hospital Insurance (or Part A) and Supplementary Medical Insurance (or Part B)",
        "Original Medicare Part A and Part B Beneficiaries", "`bene_ab_orig`", "Count of Original Medicare beneficiaries enrolled in Hospital Insurance (or Part A) and Supplementary Medical Insurance (or Part B)",
        "Medicare Advantage and Other Health Plan Part A and Part B Beneficiaries", "`bene_ab_ma_oth`", "Count of Medicare Advantage and Other Health Plan beneficiaries enrolled in Hospital Insurance (or Part A) and Supplementary Medical Insurance (or Part B)",
        "Total Medicare Part D beneficiaries", "`bene_rx_total`", "Count of all Medicare Prescription Drug (or Part D) beneficiaries",
        "Total Medicare Prescription Drug Plan beneficiaries", "`bene_rx_pdp`", "Count of Medicare Prescription Drug (or Part D) beneficiaries enrolled in a Prescription Drug Plan",
        "Total Medicare Advantage Prescription Drug Plan beneficiaries", "`bene_rx_mapd`", "Count of Medicare Prescription Drug (or Part D) beneficiaries enrolled in a Medicare Advantage Prescription Drug plan") |> 
  dplyr::select(Variable, Description, Definition) |> 
  provider:::gt_datadict()
```


<br>

## Related Links

   - [Medicare Monthly Enrollment API](https://data.cms.gov/summary-statistics-on-beneficiary-enrollment/medicare-and-medicaid-reports/medicare-monthly-enrollment)
