---
title: "CMS Open Payments API"
output: html_document
---

```{r include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

<br>

```{r}
library(provider)
```

<br>

  > *A Public Database Intended to Create Public Transparency Into Industry-Physician Financial Relationships*

<br>

The Open Payments program is a national disclosure program that promotes a more transparent and accountable health care system. Open Payments houses a publicly accessible database of payments that reporting entities, including drug and medical device companies, make to covered recipients like physicians.

<br>

## Search Examples

```{r}
open_payments(npi = 1043218118, year = 2021) |> 
  dplyr::filter(!is.na(covered)) |> 
  janitor::remove_empty(which = c("rows", "cols")) |> 
  knitr::kable()
```

<br><br>

<details><summary>Code for table</summary>

```{r}
gt_ex <- open_payments(npi = 1043218118, 
                       year = 2021) |> 
  dplyr::filter(!is.na(covered)) |> 
  janitor::remove_empty(which = c("rows", "cols")) |> 
  dplyr::filter(group == "1") |> 
  dplyr::group_by(year, 
                  payer_name,
                  pay_nature,
                  pay_form,
                  category) |> 
  dplyr::summarise(payments = dplyr::n(),
                   amount = sum(pay_total), 
                   .groups = "drop") |> 
  dplyr::arrange(dplyr::desc(amount))

gt_ex <- gt_ex |> 
  gt::gt() |> 
  gtExtras::gt_theme_538() |> 
  gt::tab_style(
    style = gt::cell_text(font = c(
      gt::google_font(name = "Fira Code"), 
      gt::default_fonts())),
    locations = gt::cells_body(columns = c(year, amount))) |> 
  gt::cols_hide(year) |> 
  gt::cols_label(payer_name = "Payer", 
                 pay_form = "Form",
                 pay_nature = "Nature", 
                 category = "Category", 
                 payments = "Payments", 
                 amount = "Amount") |> 
  gtExtras::gt_add_divider(columns = c("payer_name", "category"), 
                           style = "solid",
                           color = "black",
                           weight = gt::px(3),
                           include_labels = FALSE) |> 
  gt::tab_header(title = gt::md("CMS Open Payments Disclosure Summary: 2021"),
    subtitle = gt::md("Provider Eligibility to Refer Patients to **Medicare Part B**, 
                      **Home Health Agencies**, **Durable Medical Equipment Suppliers**, 
                      and **Powered Mobility Devices**")) |> 
  gt::tab_source_note(source_note = "Source: www.cms.gov/OpenPayments")
#|> gt::opt_table_font(font = gt::google_font(name = "Karla"))
```

</details>

```{r, echo=FALSE, eval=TRUE}
gt_ex |> gt::tab_options(table.width = gt::pct(100))
```

<br><br>

```{r}
ex <- 2016:2021 |>  
  purrr::map(open_payments, npi = 1043218118) |> 
  purrr::list_rbind()
ex |> 
  dplyr::filter(!is.na(covered)) |> 
  janitor::remove_empty(which = c("rows", "cols"))
```

<br><br>

```{r}
open_payments(npi = 1043218118, year = 2019) |> 
  dplyr::filter(!is.na(covered)) |> 
  janitor::remove_empty(which = c("rows", "cols"))
```

<br><br>

```{r}
open_payments(city = "Jacksonville", state = "FL", year = 2020) |> 
  dplyr::filter(!is.na(covered)) |> 
  janitor::remove_empty(which = c("rows", "cols"))
```

<br><br>

```{r}
open_payments(payer_id = 100000151589, year = 2020) |> 
  dplyr::filter(!is.na(covered)) |> 
  janitor::remove_empty(which = c("rows", "cols"))
```

<br><br>

## Open Payments Glossary

### Applicable Group Purchasing Organization (GPO)

Applicable group purchasing organizations (GPOs) are entities that operate in the United States and purchase, arrange for or negotiate the purchase of covered drugs, devices, biologicals, or medical supplies for a group of individuals or entities, but not solely for use by the entity itself.

### Applicable Manufacturers

Applicable manufacturers are entities that operate in the United States and (1) are engaged in the production, preparation, propagation, compounding, or conversion of a covered drug, device, biological, or medical supply, but not if such covered drug, device, biological or medical supply is solely for use by or within the entity itself or by the entity's own patients (this definition does not include distributors or wholesalers (including, but not limited to, repackagers, relabelers, and kit assemblers) that do not hold title to any covered drug, device, biological or medical supply); or (2) are entities under common ownership with an entity described in part (1) of this definition, which provides assistance or support to such entities with respect to the production, preparation, propagation, compounding, conversion, marketing, promotion, sale, or distribution of a covered drug, device, biological or medical supply. (See 42 CFR 403.902)

### Covered Recipients

Any physician, physician assistant, nurse practitioner, clinical nurse specialist, certified registered nurse anesthetist, or certified nurse-midwife who is not a bona fide employee of the applicable manufacturer that is reporting the payment; or a teaching hospital, which is any institution that received a payment under 1886(d)(5)(B), 1886(h), or 1886(s) of the Act during the last calendar year for which such information is available.

### Natures of Payment

Natures of payment categories are categories that must be used to describe why a payment or other transfer of value was made (See 42 CFR 403.904(e)(2)). They are only applicable to the “general” payment type, not research or ownership. The categories are:

   * Acquisitions (applicable to Program Year 2021 and subsequent program years)
   * Charitable contributions
   * Compensation for services other than consulting, including serving as faculty or as a speaker at an event other than a continuing education program
   * Compensation for serving as faculty or as a speaker for an accredited or certified continuing education program (Applicable to Program Years 2013 - 2020)
   * Compensation for serving as faculty or as a speaker for an unaccredited and non-certified continuing education program (Applicable to Program Years 2013 - 2020)
   * Compensation for serving as faculty or as a speaker for medical education program (Applicable beginning with Program Year 2021 and subsequent program years)
   * Consulting fees
   * Current or prospective ownership or investment interest (to be removed starting in Program Year 2023)
   * Debt Forgiveness (Applicable beginning with Program Year 2021 and subsequent program years)
   * Education
   * Entertainment
   * Food and beverage
   * Gift
   * Grant
   * Honoraria
   * Long-term medical supply or device loan (Applicable beginning with Program Year 2021 and subsequent program years)
   * Royalty or license
   * Space rental or facility fees (teaching hospitals only)
   * Travel and lodging
   
### National Provider Identifier (NPI)

The NPI is a unique identification number for covered health care providers. The NPI is a 10-position numeric identifier, with a check digit in the 10th position and no intelligence about the health care provider in the number. (See 45 CFR 162.406)

### Newly Added Covered Recipients

Open Payments expanded in January 2021 to include five new provider types: 

   1. **Physician Assistants**: A physician assistant who performs such services as such individual is legally authorized to perform (in the State in which the individual performs such services) in accordance with State law (or the State regulatory mechanism provided by State law), and who meets such training, education, and experience requirements (or any combination thereof) as the Secretary may prescribe in regulations.
   2. **Nurse Practitioners**: A nurse practitioner who performs such services as such individual is legally authorized to perform (in the State in which the individual performs such services) in accordance with State law (or the State regulatory mechanism provided by State law), and who meets such training, education, and experience requirements (or any combination thereof) as the Secretary may prescribe in regulations.
   3. **Clinical Nurse Specialists**: An individual who is a registered nurse and is licensed to practice nursing in the State in which the clinical nurse specialist services are performed; and holds a master’s degree in a defined clinical area of nursing from an accredited educational institution.
   4. **Certified Registered Nurse Anesthetists**: A certified registered nurse anesthetist licensed by the State who meets such education, training, and other requirements relating to anesthesia services and related care as the Secretary may prescribe. In prescribing such requirements the Secretary may use the same requirements as those established by a national organization for the certification of nurse anesthetists. Such term also includes, as prescribed by the Secretary, an **Anesthesiologist Assistant**.
   5. **Certified Nurse-Midwives**: A registered nurse who has successfully completed a program of study and clinical experience meeting guidelines prescribed by the Secretary, or has been certified by an organization recognized by the Secretary.

### Non-Physician Practitioner Covered Recipient

Health care providers who practice either in collaboration with or under the supervision of a physician, including physician assistants, nurse practitioners, and clinical nurse specialists, are referred to as non-physician practitioners (NPPs).

### Ownership or Investment Interest

Ownership and investment interest includes, but is not limited to:

   * Stock
   * Stock option(s) (other than those received as compensation, until they are exercised)
   * Partnership share(s)
   * Limited liability company membership(s)
   * Loans
   * Bonds
   * Other financial instruments that are secured with an entity’s property or revenue or a portion of that property or revenue

This may be direct or indirect and through debt, equity or other means (See 42 CFR 403.902). Please note that there are exceptions to the definition.

### Physician

For the purposes of Open Payments, a “physician” is any of the following types of professionals that are legally authorized by the state to practice, regardless of whether they are Medicare, Medicaid, or Children's health Insurance Program (CHIP) providers:

   * Doctors of Medicine or Osteopathic Medicine
   * Doctors of Dental Medicine or Dental Surgery
   * Doctors of Podiatric Medicine
   * Doctors of Optometry
   * Chiropractors
   
   *Note: Medical residents are excluded from the definition of physicians for the purpose of this program.*

### Reporting Entities

Reporting entities are applicable manufacturers or applicable GPOs.

### Research

Research is a systematic investigation to develop or contribute to generalized knowledge about public health, including behavioral and social-sciences research. This definition includes basic and applied research, and product development. (See 42 CFR 403.902)

### Teaching Hospital

Teaching hospitals are hospitals that receive payment for Medicare direct graduate medical education (GME), IPPS indirect medical education (IME), or psychiatric hospital IME programs during the last calendar year for which such information is available. (See 42 CFR 403.902) For the purposes of Open Payments, “teaching hospitals” are hospitals that received payment for Medicare direct graduate medical education (GME), inpatient prospective payment system (IPPS) indirect medical education (IME), or psychiatric hospital IME programs during the last calendar year for which such information is available.

### Third Parties

Third parties are other individuals or entities, whether or not they operate in the United States.

### Transfers of Value

Payments or other transfers of value are anything of value given by an applicable manufacturer or applicable GPO to a covered recipient or physician owner/investor that does not fall within one of the excluded categories in the rule. (See 42 CFR 403.902)

<br><br>


### Related Links

   - [Natures of Payment](https://www.cms.gov/OpenPayments/Natures-of-Payment)
   - [Law and Policy](https://www.cms.gov/OpenPayments/Law-and-Policy)
   - [Audits and Penalties](https://www.cms.gov/OpenPayments/Program-Participants/Reporting-Entities/Audits-and-Penalties)
   - [Reporting Entities](https://www.cms.gov/openpayments/program-participants/reporting-entities)
   - [Open Payments: General Resources](https://www.cms.gov/OpenPayments/Resources)

<br><br>
