---
title: "Linking Providers"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 600, 
  out.width = "100%"
)
options(scipen = 999)
library(provider)
library(vctrs)
library(purrr)
library(gt)
```

## NPIs, PACs, ENIDs, CCNs, CLIAs and Many More

```{r}
pac <- affiliations(pac = 7810891009)
gt(pac, rownames_to_stub = TRUE) |> 
  opt_table_font(font = google_font(name = "JetBrains Mono"), size = gt::px(12))
```


```{r}
ccn <- hospitals(ccn = unique(pac$facility_ccn))
gt(ccn, 
   groupname_col = "org_name", 
   rowname_col = "dba_name", 
   row_group_as_column = TRUE, 
   rownames_to_stub = TRUE) |> 
  opt_table_font(
    font = google_font(name = "JetBrains Mono"), 
    size = px(12))
```


<br>

Exploring links between providers can lead to many interesting insights. For example, there is a hospital in New York named **Elizabethtown Community Hospital**. 

```{r}
providers(org_name = "Elizabethtown Community Hospital") |> 
  gt(rownames_to_stub = TRUE) |> 
  opt_table_font(
    font = google_font(name = "JetBrains Mono"), 
    size = px(12))
```



```{r}
hospitals(org_name = "Elizabethtown Community Hospital") |> 
  gt(rownames_to_stub = TRUE) |> 
  opt_table_font(
    font = google_font(name = "JetBrains Mono"), 
    size = px(12))
```

<br>

The **Hospital Enrollment** API includes only Medicare Part A (hospital) providers, so we only get two rows back, but those include a new data point: two facility CCNs. Plugging those into the **Facility Affiliations** API, we can retrieve information on the individual providers practicing at this hospital. First, the all-numeric CCN (`331302`):

<br>

```{r}
affiliations(facility_ccn = 331302) |> 
  gt(rownames_to_stub = TRUE) |> 
  opt_table_font(
    font = google_font(name = "JetBrains Mono"), 
    size = px(12))
```


<br>

That returns individual providers affiliated with the hospital. Now to search the alphanumeric CCN (`33Z302`):


```{r}
affiliations(facility_ccn = "33Z302") |> 
  gt(rownames_to_stub = TRUE) |> 
  opt_table_font(
    font = google_font(name = "JetBrains Mono"), 
    size = px(12))
```

<br>

That returns more affiliated individual providers that practice in the Hospital's nursing home..

<br>

> An *alphanumeric* CCN represents a sub-unit of the hospital, here a nursing home. We would get the same result if we'd set the `parent_ccn` argument to the numeric CCN, i.e. `affiliations(parent_ccn = 331302)`

