---
title: "Linking Providers"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE, 
  message   = TRUE, 
  warning   = TRUE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 600, 
  out.width = "100%"
)
options(scipen = 999)
library(tibble)
```

```{r}
library(provider)
```


> NPIs, PACs, ENIDs, CCNs, CLIAs and Many More

#### Individual Provider

```{r}
pac <- affiliations(pac = 7810891009)
list(
  individual = as.data.frame(t(unique(pac[1:6]))),
  organization = pac[7:9])
```


```{r}
ccn <- hospitals(ccn = pac$facility_ccn)
ccn |> str()
```

<br>

#### Organizational Provider

Exploring links between providers can lead to many interesting insights. For example, there is a hospital in New York named **Elizabethtown Community Hospital**. 

```{r}
providers(org_name = "Elizabethtown Community Hospital")
```

```{r}
hospitals(org_name = "Elizabethtown Community Hospital")
```

```{r}
clinicians(org_name = "Elizabethtown Community Hospital")
```

```{r}
reassignments(org_name = "Elizabethtown Community Hospital")
```

<br>

The **Hospital Enrollment** API includes only Medicare Part A (hospital) providers, so we only get two rows back, but those include a new data point: two facility CCNs. Plugging those into the **Facility Affiliations** API, we can retrieve information on the individual providers practicing at this hospital. First, the all-numeric CCN (`331302`):

<br>

```{r}
ccn <- affiliations(facility_ccn = 331302)
list(
  organization = as.data.frame(t(unique(ccn[7:9]))),
  individual = unique(ccn[1:6])
  )
```


<br>

That returns individual providers affiliated with the hospital. Now to search the alphanumeric CCN (`33Z302`):


```{r}
ccn2 <- affiliations(facility_ccn = "33Z302")
list(
  organization = as.data.frame(t(unique(ccn2[7:9]))),
  individual = unique(ccn2[1:6])
  )
```

<br>

That returns more affiliated individual providers that practice in the Hospital's nursing home..

<br>

> An *alphanumeric* CCN represents a sub-unit of the hospital, here a nursing home. We would get the same result if we'd set the `parent_ccn` argument to the numeric CCN, i.e. `affiliations(parent_ccn = 331302)`

