---
title: "Linking Providers"
description: "NPIs, PAC IDs, Enrollment IDs, CCNs, CLIAs and More"
author: "Andrew Bruce"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 600, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
options(scipen = 999)
```


```{r message=FALSE, warning=FALSE}
library(provider)
library(tibble)
library(vctrs)
library(dplyr)
library(purrr)
library(gt)
```


<br>

## Individual Provider

```{r}
vctrs::vec_rbind(
  display_long(providers(pac = 7810891009)) |> tibble::add_column(source = "`providers()`"),
  display_long(reassignments(pac = 7810891009)) |> tibble::add_column(source = "`reassignments()`"),
  display_long(clinicians(pac = 7810891009)) |> tibble::add_column(source = "`clinicians()`"),
  display_long(nppes(npi = 1043245657)) |> tibble::add_column(source = "`nppes()`"),
  display_long(order_refer(npi = 1043245657)) |> tibble::add_column(source = "`order_refer()`")) |> 
  distinct(name, value, .keep_all = TRUE) |> 
  gt(groupname_col = "source", 
     row_group_as_column = TRUE, process_md = TRUE) |> 
  opt_table_font(font = google_font(name = "JetBrains Mono")) |> 
  tab_options(column_labels.hidden = TRUE, 
              table.width = px(600),
              heading.background.color = "black",
              heading.align = "left", 
              stub_row_group.font.weight = "bold") |> 
  tab_header(title = md("**PROVIDER**: Mark, K. Fung, M.D.")) |> 
  opt_horizontal_padding(scale = 2) |> 
  opt_all_caps()
```

<br>

```{r}
affiliations(pac = 7810891009) |> 
  pull(facility_ccn) |>
  map_dfr(~hospitals(facility_ccn = .x)) |> 
  select(-reh_conversion) |> 
  display_long(cols = !organization) |> 
  filter(!is.na(value)) |> 
  gt(groupname_col = "organization", 
     row_group_as_column = TRUE) |> 
  opt_table_font(font = google_font(name = "JetBrains Mono")) |> 
  tab_options(column_labels.hidden = TRUE, 
              table.width = px(800),
              heading.background.color = "black",
              heading.align = "left", 
              stub_row_group.font.weight = "bold") |> 
  tab_header(title = md("**FACILITY** AFFILIATIONS")) |> 
  opt_horizontal_padding(scale = 2) |> 
  opt_all_caps()
```


<br>

Exploring links between providers can lead to many interesting insights. For example, there is a hospital in New York named **Elizabethtown Community Hospital**. 

```{r}
providers(organization = "Elizabethtown Community Hospital") |> 
  gt_preview(top_n = 10) |> 
  opt_table_font(font = google_font(name = "JetBrains Mono"))
```



```{r}
hospitals(organization = "Elizabethtown Community Hospital") |> 
  gt_preview(top_n = 10) |> 
  opt_table_font(font = google_font(name = "JetBrains Mono"))
```

<br>

The **Hospital Enrollment** API includes only Medicare Part A (hospital) providers, so we only get two rows back, but those include a new data point: two facility CCNs. Plugging those into the **Facility Affiliations** API, we can retrieve information on the individual providers practicing at this hospital. First, the all-numeric CCN (`331302`):

<br>

```{r}
affiliations(facility_ccn = 331302) |> 
  gt_preview(top_n = 20) |> 
  opt_table_font(font = google_font(name = "JetBrains Mono"))
```


<br>

That returns individual providers affiliated with the hospital. Now to search the alphanumeric CCN (`33Z302`):


```{r}
affiliations(facility_ccn = "33Z302") |> 
  gt_preview(top_n = 10) |> 
  opt_table_font(font = google_font(name = "JetBrains Mono"))
```

<br>

That returns more affiliated individual providers that practice in the Hospital's nursing home..

<br>

> An *alphanumeric* CCN represents a sub-unit of the hospital, here a nursing home. We would get the same result if we'd set the `parent_ccn` argument to the numeric CCN, i.e. `affiliations(parent_ccn = 331302)`

