---
title: "Linking Providers"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE, 
  message   = TRUE, 
  warning   = TRUE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 600, 
  out.width = "100%"
)
options(scipen = 999)
library(tibble)
```

```{r}
library(provider)
```

#### Individual Provider

```{r}
x <- affiliations(pac = 7810891009)
x <- list(
  individual = as.data.frame(t(unique(x[1:4]))),
  organization = hospitals(ccn = x$prov_ccn))
x

reassignments(pac = 7810891009) |> str()

clinicians(pac = 7810891009) |> str()
```

#### Organizational Provider

```{r}
x <- "Elizabethtown Community Hospital"

hospitals(org_name = x) |> str()

clinicians(org_name = x) |> str()

reassignments(org_name = x)
```

The **Hospital Enrollment** API includes only Medicare Part A (hospital)
providers, so we only get two rows back, but those include a new data point: two
facility CCNs. Plugging those into the **Facility Affiliations** API, we can
retrieve information on the individual providers practicing at this hospital.
First, the all-numeric CCN (`331302`):

```{r}
ccn <- affiliations(facility_ccn = 331302)

list(
  organization = as.data.frame(t(unique(ccn[5:7]))),
  individual = unique(ccn[1:4]))
```

That returns individual providers affiliated with the hospital. Now to search
the alphanumeric CCN (`33Z302`):

```{r}
ccn2 <- affiliations(facility_ccn = "33Z302")

list(
  organization = as.data.frame(t(unique(ccn2[5:7]))), 
  individual = unique(ccn2[1:4]))
```

That returns more affiliated individual providers that practice in the
Hospital's nursing home.

> An *alphanumeric* CCN represents a `sub-unit` of the hospital, here a nursing
home. We would get the same result if we'd set the `parent_ccn` argument to the
numeric CCN, i.e. `affiliations(parent_ccn = 331302)`

