---
title: "Medicare Order and Referring API"
output: html_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

```{r}
library(provider)
```

<br>

## Medicare Order and Referring API

<br>

The Order and Referring dataset provides information on all physicians and non-physician practitioners, by their National Provider Identifier (NPI), who are of a type/specialty that is legally eligible to order and refer in the Medicare program and who have current enrollment records in Medicare. This dataset is based on information gathered from the Provider Enrollment, Chain and Ownership System (PECOS).

<br>

 - [Medicare Order and Referring API](https://data.cms.gov/provider-characteristics/medicare-provider-supplier-enrollment/order-and-referring)

```{r}
order_refer(1003026055)
```

<br>

### Data Dictionary

```{r echo=FALSE}
tibble::tibble(
  Variable = c(
    "`npi`", "`last_name`", "`first_name`", "`partb`", "`dme`",
    "`hha`", "`pmd`"
  ),
  Term = c("NPI", "Last Name", "First Name", "Part B", "DME", "HHA", "PMD"),
  Definition = c(
    "National Provider Identifier (NPI) of the Order and Referring Provider",
    "Last Name of the Order and Referring Provider", 
    "First Name of the Order and Referring Provider",
    "Indicates if Provider can refer to Medicare Part B", 
    "Indicates if Provider can order Durable Medical Equipment (DME)",
    "Indicates if Provider can refer to a Home Health Agency (HHA)", 
    "Indicates if Provider can order Power Mobility Devices (PMDs)"
  )) |>
  gt::gt() |> 
  gt::fmt_markdown(columns = Variable) |> 
  gtExtras::gt_theme_nytimes() |> 
  gt::opt_stylize(style = 4, color = "gray", add_row_striping = FALSE) |> 
  gt::opt_table_lines(extent = "default") |> 
  gt::opt_table_outline(style = "none")
```

<br>

### Further Reading

   - [Endpoints Information](https://nppes.cms.hhs.gov/webhelp/nppeshelp/HEALTH%20INFORMATION%20EXCHANGE.html)
   - [CMS Public Reporting of Missing Digital Contact Information](https://data.cms.gov/provider-compliance/public-reporting-of-missing-digital-contact-information)

<br><br>
