---
title: "Medicare Public Provider Enrollment API"
output: html_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

```{r}
library(provider)
```

<br>

> *Information on a point-in-time snapshot of enrollment-level data for Providers actively enrolled in Medicare.*

<br>

The Medicare Fee-For-Service Public Provider Enrollment dataset includes information on providers who are actively approved to bill Medicare or have completed the 855O at the time the data was pulled from the [Provider Enrollment and Chain Ownership System](https://pecos.cms.hhs.gov) (PECOS). 

These files are populated from PECOS and contain basic enrollment and provider information, reassignment of benefits information and practice location city, state and zip. These files are not intended to be used as real time reporting as the data changes from day to day and the files are updated only on a quarterly basis. This data does not include information on opt-out providers. Information is redacted where necessary to protect Medicare provider privacy.

<br>

## Example

```{r}
provider_enrollment(npi = 1003026055)
```


<br>

### Data Dictionary

```{r echo=FALSE}
tibble::tibble(
  Variable = c(
    "`npi`", "`pecos_asct_cntl_id`", "`enrlmt_id`", "`provider_type_cd`",
    "`provider_type_desc`", "`state_cd`", "`first_name`", "`mdl_name`",
    "`last_name`", "`org_name`", "`gndr_sw`", "`reasgn_bnft_enrlmt_id`",
    "`rcv_bnft_enrlmt_id`", "`city_name`", "`zip_cd`"
  ),
  Description = c(
    "National Provider Identifier", "PECOS Associate Control ID",
    "Enrollment ID", "Provider Type Code", "Provider Type Description",
    "State Code", "First Name", "Middle Name", "Last Name", "Organization Name",
    "Gender", "Reassigning Benefits Enrollment ID", "Receiving Benefits Enrollment ID",
    "City Name", "Zip Code"
  ),
  Definition = c(
    "An NPI is a 10-digit unique numeric identifier that all providers must obtain before enrolling in Medicare. It is assigned to health care providers upon application through the National Plan and Provider Enumeration System (NPPES).",
    "Provider associate level variable (PAC ID) from PECOS database used to link across tables. A PAC ID is a 10-digit unique numeric identifier that is assigned to each individual or organization in PECOS. All entity-level information (e.g., tax identification numbers and organizational names) is linked through the PAC ID. A PAC ID may be associated with multiple Enrollment IDs if the individual or organization enrolled multiple times under different circumstances.",
    "Provider enrollment ID from PECOS database used to link across tables. An Enrollment ID is a 15-digit unique alphanumeric identifier that is assigned to each new provider enrollment application. All enrollment-level information (e.g., enrollment type, enrollment state, provider specialty and reassignment of benefits) is linked through the Enrollment ID.",
    "Provider enrollment application and enrollment specialty type, see PROVIDER_TYPE_CD - Reference for description of values. This field shows the provider’s primary specialty code. For practitioners and DME suppliers, please see the Secondary Specialty file for a list of secondary specialties (when applicable). Only about 20% of practitioners and DME suppliers have at least one secondary specialty.",
    "Provider enrollment application and enrollment specialty type description, see PROVIDER_TYPE_CD - Reference for description of values.",
    "Provider enrollment state, abbreviated location, see STATE_CD - Reference tab for description of values. Providers enroll at the state level, so one PAC ID may be associated with multiple ENRLMT_IDs and multiple STATE_CD values.",
    "Individual provider first name.", "Individual provider middle name.",
    "Individual provider last name.", "Organizational provider name.",
    "Individual provider gender, see GNDR_SW - Reference for description of values.",
    "Enrollment ID of the provider reassigning benefits to bill to Medicare. To find enrollment information for providers reassigning their benefits to bill to Medicare, link REASGN_BNFT_ENRLMT_ID to ENRLMT_ID in the Enrollment file.",
    "Enrollment ID of the provider receiving reassignment benefits to bill to Medicare. To find enrollment information for providers receiving reassignment benefits to bill to Medicare, link RCV_BNFT_ENRLMT_ID to ENRLMT_ID in the Enrollment file.",
    "Provider practice location city. Each practice location is linked to an Enrollment ID. If any other provider reassigns benefits to an Enrollment ID listed in the Practice Location file, the practice location is also associated with that other provider.",
    "Provider practice location zip code. Each practice location is linked to an Enrollment ID. If any other provider reassigns benefits to an Enrollment ID listed in the Practice Location file, the practice location is also associated with that other provider."
  )) |>
  gt::gt() |> 
  gt::fmt_markdown(columns = Variable) |> 
  gtExtras::gt_theme_nytimes() |> 
  gtExtras::gt_merge_stack(col1 = Description, 
                           col2 = Definition,
                           small_cap = FALSE,
                           font_size = c("16px", "14px"),
                           font_weight = c("bold", "normal"),
                           palette = c("black", "darkgray")) |> 
  gt::opt_stylize(style = 4, color = "gray", add_row_striping = FALSE) |> 
  gt::opt_table_lines(extent = "default") |> 
  gt::opt_table_outline(style = "none")
```

<br>



```{r echo=FALSE, eval=FALSE}
#### Provider Type Code List
cd <- tibble::tibble(
  Code = c(
    "`00-00`", "`00-01`", "`00-02`", "`00-03`", "`00-04`", "`00-05`",
    "`00-06`", "`00-07`", "`00-08`", "`00-09`", "`00-10`", "`00-13`",
    "`00-14`", "`00-17`", "`00-18`", "`00-19`", "`00-85`", "`12-23`",
    "`12-31`", "`12-45`", "`12-47`", "`12-49`", "`12-59`", "`12-60`",
    "`12-61`", "`12-63`", "`12-65`", "`12-69`", "`12-70`", "`12-73`",
    "`12-74`", "`12-75`", "`12-87`", "`12-C0`", "`12-C1`", "`12-Z1`",
    "`12-Z3`", "`12-Z4`", "`12-Z5`", "`14-01`", "`14-02`", "`14-03`",
    "`14-04`", "`14-05`", "`14-06`", "`14-07`", "`14-08`", "`14-09`",
    "`14-10`", "`14-11`", "`14-12`", "`14-13`", "`14-14`", "`14-15`",
    "`14-16`", "`14-17`", "`14-18`", "`14-19`", "`14-20`", "`14-21`",
    "`14-22`", "`14-23`", "`14-24`", "`14-25`", "`14-26`", "`14-27`",
    "`14-28`", "`14-29`", "`14-30`", "`14-32`", "`14-33`", "`14-34`",
    "`14-35`", "`14-36`", "`14-37`", "`14-38`", "`14-39`", "`14-40`",
    "`14-41`", "`14-42`", "`14-43`", "`14-44`", "`14-46`", "`14-48`",
    "`14-50`", "`14-62`", "`14-64`", "`14-65`", "`14-66`", "`14-67`",
    "`14-68`", "`14-70`", "`14-71`", "`14-72`", "`14-73`", "`14-76`",
    "`14-77`", "`14-78`", "`14-79`", "`14-80`", "`14-81`", "`14-82`",
    "`14-83`", "`14-84`", "`14-85`", "`14-86`", "`14-88`", "`14-89`",
    "`14-90`", "`14-91`", "`14-92`", "`14-93`", "`14-94`", "`14-97`",
    "`14-98`", "`14-99`", "`14-99`", "`14-C0`", "`14-C3`", "`30-01`",
    "`30-02`", "`30-03`", "`30-04`", "`30-05`", "`30-06`", "`30-07`",
    "`30-08`", "`30-11`", "`30-12`", "`30-13`", "`30-14`", "`30-16`",
    "`30-18`", "`30-19`", "`30-20`", "`30-23`", "`30-24`", "`30-25`",
    "`30-26`", "`30-29`", "`30-30`", "`30-34`", "`30-35`", "`30-37`",
    "`30-38`", "`30-40`", "`30-41`", "`30-44`", "`30-46`", "`30-48`",
    "`30-49`", "`30-50`", "`30-51`", "`30-52`", "`30-53`", "`30-54`",
    "`30-55`", "`30-56`", "`30-57`", "`30-58`", "`30-59`", "`30-61`",
    "`30-63`", "`30-64`", "`30-65`", "`30-66`", "`30-67`", "`30-70`",
    "`30-72`", "`30-76`", "`30-77`", "`30-79`", "`30-82`", "`30-83`",
    "`30-84`", "`30-85`", "`30-87`", "`30-88`", "`30-89`", "`30-90`",
    "`30-91`", "`30-92`", "`30-93`", "`30-94`", "`30-95`", "`30-96`",
    "`30-97`", "`30-99`", "`30-A0`", "`30-A1`", "`30-A2`", "`30-A3`",
    "`30-A4`", "`30-A5`", "`30-A6`", "`30-A7`", "`30-A8`", "`30-A9`",
    "`30-B1`", "`30-B2`", "`30-B3`", "`30-B4`", "`30-B5`", "`30-C0`",
    "`33-01`", "`33-02`", "`33-03`", "`33-04`", "`33-05`", "`33-06`",
    "`33-07`", "`33-08`", "`33-09`", "`33-10`", "`33-11`", "`33-12`",
    "`33-13`", "`33-14`", "`33-16`", "`33-17`", "`33-18`", "`33-19`",
    "`33-20`", "`33-21`", "`33-22`", "`33-23`", "`33-24`", "`33-25`",
    "`33-26`", "`33-27`", "`33-28`", "`33-29`", "`33-30`", "`33-33`",
    "`33-34`", "`33-35`", "`33-36`", "`33-37`", "`33-38`", "`33-39`",
    "`33-40`", "`33-41`", "`33-42`", "`33-43`", "`33-44`", "`33-46`",
    "`33-48`", "`33-50`", "`33-62`", "`33-66`", "`33-68`", "`33-71`",
    "`33-72`", "`33-76`", "`33-77`", "`33-78`", "`33-79`", "`33-80`",
    "`33-81`", "`33-82`", "`33-83`", "`33-84`", "`33-85`", "`33-86`",
    "`33-88`", "`33-89`", "`33-90`", "`33-91`", "`33-92`", "`33-93`",
    "`33-94`", "`33-97`", "`33-98`", "`33-99`", "`33-C0`", "`33-C3`",
    "`53-D1`"
  ),
  Type = c(
    "Part A Provider", "Part A Provider", "Part A Provider", "Part A Provider",
    "Part A Provider", "Part A Provider", "Part A Provider", "Part A Provider",
    "Part A Provider", "Part A Provider", "Part A Provider", "Part A Provider",
    "Part A Provider", "Part A Provider", "Part A Provider", "Part A Provider",
    "Part A Provider", "Part B Supplier", "Part B Supplier", "Part B Supplier",
    "Part B Supplier", "Part B Supplier", "Part B Supplier", "Part B Supplier",
    "Part B Supplier", "Part B Supplier", "Part B Supplier", "Part B Supplier",
    "Part B Supplier", "Part B Supplier", "Part B Supplier", "Part B Supplier",
    "Part B Supplier", "Part B Supplier", "Part B Supplier", "Part B Supplier",
    "Part B Supplier", "Part B Supplier", "Part B Supplier", "Practitioner",
    "Practitioner", "Practitioner", "Practitioner", "Practitioner",
    "Practitioner", "Practitioner", "Practitioner", "Practitioner",
    "Practitioner", "Practitioner", "Practitioner", "Practitioner",
    "Practitioner", "Practitioner", "Practitioner", "Practitioner",
    "Practitioner", "Practitioner", "Practitioner", "Practitioner",
    "Practitioner", "Practitioner", "Practitioner", "Practitioner",
    "Practitioner", "Practitioner", "Practitioner", "Practitioner",
    "Practitioner", "Practitioner", "Practitioner", "Practitioner",
    "Practitioner", "Practitioner", "Practitioner", "Practitioner",
    "Practitioner", "Practitioner", "Practitioner", "Practitioner",
    "Practitioner", "Practitioner", "Practitioner", "Practitioner",
    "Practitioner", "Practitioner", "Practitioner", "Practitioner",
    "Practitioner", "Practitioner", "Practitioner", "Practitioner",
    "Practitioner", "Practitioner", "Practitioner", "Practitioner",
    "Practitioner", "Practitioner", "Practitioner", "Practitioner",
    "Practitioner", "Practitioner", "Practitioner", "Practitioner",
    "Practitioner", "Practitioner", "Practitioner", "Practitioner",
    "Practitioner", "Practitioner", "Practitioner", "Practitioner",
    "Practitioner", "Practitioner", "Practitioner", "Practitioner",
    "Practitioner", "Practitioner", "Practitioner", "DME Supplier",
    "DME Supplier", "DME Supplier", "DME Supplier", "DME Supplier",
    "DME Supplier", "DME Supplier", "DME Supplier", "DME Supplier",
    "DME Supplier", "DME Supplier", "DME Supplier", "DME Supplier",
    "DME Supplier", "DME Supplier", "DME Supplier", "DME Supplier",
    "DME Supplier", "DME Supplier", "DME Supplier", "DME Supplier",
    "DME Supplier", "DME Supplier", "DME Supplier", "DME Supplier",
    "DME Supplier", "DME Supplier", "DME Supplier", "DME Supplier",
    "DME Supplier", "DME Supplier", "DME Supplier", "DME Supplier",
    "DME Supplier", "DME Supplier", "DME Supplier", "DME Supplier",
    "DME Supplier", "DME Supplier", "DME Supplier", "DME Supplier",
    "DME Supplier", "DME Supplier", "DME Supplier", "DME Supplier",
    "DME Supplier", "DME Supplier", "DME Supplier", "DME Supplier",
    "DME Supplier", "DME Supplier", "DME Supplier", "DME Supplier",
    "DME Supplier", "DME Supplier", "DME Supplier", "DME Supplier",
    "DME Supplier", "DME Supplier", "DME Supplier", "DME Supplier",
    "DME Supplier", "DME Supplier", "DME Supplier", "DME Supplier",
    "DME Supplier", "DME Supplier", "DME Supplier", "DME Supplier",
    "DME Supplier", "DME Supplier", "DME Supplier", "DME Supplier",
    "DME Supplier", "DME Supplier", "DME Supplier", "DME Supplier",
    "DME Supplier", "DME Supplier", "DME Supplier", "DME Supplier",
    "DME Supplier", "DME Supplier", "DME Supplier", "DME Supplier",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "Order And Referring Only", "Order And Referring Only", "Order And Referring Only",
    "MDPP Supplier"
  ),
  Subtype = c(
    "Religious Non-Medical Health Care Institution (RNHCI)", "Community Mental Health Center",
    "Comprehensive Outpatient Rehabilitation Facility", "End-Stage Renal Disease Facility (Esrd)",
    "Federally Qualified Health Center (FQHC)", "Histocompatibility Laboratory",
    "Home Health Agency", "Home Health Agency (Subunit)", "Hospice",
    "Hospital", "Indian Health Services Facility", "Organ Procurement Organization (OPO)",
    "Outpatient Physical Therapy/Occupational Therapy/Speech Pathology Services",
    "Rural Health Clinic", "Skilled Nursing Facility", "Other", "Critical Access Hospital",
    "Sports Medicine", "Intensive Cardiac Rehabilitation", "Mammography Screening Center",
    "Independent Diagnostic Testing Facility (IDTF)", "Ambulatory Surgical Center",
    "Ambulance Service Supplier", "Public Health/Welfare Agency",
    "Voluntary Health/Charity Agency", "Portable X-Ray Supplier",
    "Physical/Occupational Therapy Group In Private Practice", "Independent Clinical Laboratories (CLIA)",
    "Clinic/Group Practice", "Mass Immunization (Roster Biller Only)",
    "Radiation Therapy Center", "Slide Preparation Facilities", "Other",
    "Sleep Laboratory/Medicine", "Centralized Flu Biller", "Hospital Department(s)",
    "Medicare + Choice Organization", "Medical Faculty Practice Plan",
    "Other Medical Care Group", "General Practice", "General Surgery",
    "Allergy/Immunology", "Otolaryngology", "Anesthesiology", "Cardiovascular Disease (Cardiology)",
    "Dermatology", "Family Practice", "Interventional Pain Management",
    "Gastroenterology", "Internal Medicine", "Osteopathic Manipulative Medicine",
    "Neurology", "Neurosurgery", "Speech Language Pathologist", "Obstetrics/Gynecology",
    "Hospice/Palliative Care", "Ophthalmology", "Oral Surgery (Dentist Only)",
    "Orthopedic Surgery", "Cardiac Electrophysiology", "Pathology",
    "Sports Medicine", "Plastic And Reconstructive Surgery", "Physical Medicine And Rehabilitation",
    "Psychiatry", "Geriatric Psychiatry", "Colorectal Surgery (Proctology)",
    "Pulmonary Disease", "Diagnostic Radiology", "Anesthesiology Assistant",
    "Thoracic Surgery", "Urology", "Chiropractic", "Nuclear Medicine",
    "Pediatric Medicine", "Geriatric Medicine", "Nephrology", "Hand Surgery",
    "Optometry", "Certified Nurse Midwife", "Certified Registered Nurse Anesthetist",
    "Infectious Disease", "Endocrinology", "Podiatry", "Nurse Practitioner",
    "Psychologist Billing Independently", "Audiologist", "Physical Therapist",
    "Rheumatology", "Occupational Therapist", "Clinical Psychologist",
    "Single Or Multispecialty Clinic Or Group Practice", "Registered Dietitian Or Nutrition Professional",
    "Pain Management", "Mass Immunization Roster Biller", "Peripheral Vascular Disease",
    "Vascular Surgery", "Cardiac Surgery", "Addiction Medicine",
    "Clinical Social Worker", "Critical Care (Intensivists)", "Hematology",
    "Hematology/Oncology", "Preventative Medicine", "Maxillofacial Surgery",
    "Neuropsychiatry", "Other (Non-Physician)", "Clinical Nurse Specialist",
    "Medical Oncology", "Surgical Oncology", "Radiation Oncology",
    "Emergency Medicine", "Interventional Radiology", "Physician Assistant",
    "Gynecological Oncology", "Other (Physician)", "Other", "Sleep Laboratory/Medicine",
    "Interventional Cardiology", "Physician - General Practice",
    "Physician - General Surgery", "Physician - Allergy/Immunology",
    "Physician - Otolaryngology", "Physician - Anesthesiology", "Physician - Cardiology",
    "Physician - Dermatology", "Physician - Family Practice", "Physician - Internal Medicine",
    "Physician - Osteopathic Manipulative Medicine", "Physician - Neurology",
    "Physician - Neurosurgery", "Physician - Obstetrics/Gynecology",
    "Physician - Ophthalmology", "Oral Surgery - Dentist", "Physician - Orthopedic/Orthopedic Surgery",
    "Sports Medicine", "Physician - Plastic And Reconstructive Surgery",
    "Physician - Physical And Rehabilitation", "Physician - Psychiatry",
    "Physician - Pulmonary Disease", "Physician - Diagnostic Radiology",
    "Physician - Urology", "Physician - Chiropractic", "Physician - Pediatric Medicine",
    "Physician - Geriatric Medicine", "Physician - Hand Surgery",
    "Physician - Optometrist", "Physician - Infectious Disease",
    "Physician - Endocrinology", "Physician - Podiatry", "Ambulatory Surgical Center",
    "Nurse Practitioner", "Medical Supply Company With Orthotic Personnel",
    "Medical Supply Company With Prosthetic Personnel", "Medical Supply Company With Orthotic-Prosthetic",
    "Medical Supply Company", "Orthotic Personnel", "Prosthetic Personnel",
    "Certified Orth/Pros/Pedorthist", "Medical Supply Company With Registered Pharmacist",
    "Ambulance Service Supplier", "Voluntary Health Or Charitable Agencies",
    "Portable X-Ray Supplier", "Independently-Billing Audiologist",
    "Independently-Practicing Physical Therapist", "Physician - Rheumatology",
    "Independently-Practicing Occupational Therapist", "Multi-Specialty - Physician",
    "Physician - Interventional Pain Management", "Physician - Peripheral Vascular Disease",
    "Physician - Vascular Surgery", "Physician - Addiction Medicine",
    "Physician - Hematology", "Physician - Hematology/Oncology",
    "Physician - Preventive Medicine", "Physician - Maxillofacial Surgery",
    "Other", "Unknown Supplier/Provider", "Certified Clinical Nurse Specialist",
    "Physician - Medical Oncology", "Physician - Surgical Oncology",
    "Physician - Radiation Oncology", "Physician - Emergency Medicine",
    "Physician - Interventional Radiology", "Independent Physiological Lab",
    "Optician", "Physician Assistant", "Physician - Unknown Physician Specialty",
    "Hospital", "Nursing Facility", "Nursing Facility Intermediate Care",
    "Skilled Nursing Facility Other", "Home Health Agency", "Pharmacy",
    "Medical Supply Company With Respiratory Therapist", "Department Store",
    "Grocery Store", "Indian Health Service Or Tribal Facility",
    "Oxygen & Equipment", "Pedorthic Personnel", "Medical Supply Company With Pedorthic Personnel",
    "Rehabilitation Agency", "Ocularist", "Sleep Laboratory/Medicine",
    "General Practice", "General Surgery", "Allergy/Immunology",
    "Otolaryngology", "Anesthesiology", "Cardiovascular Disease (Cardiology)",
    "Dermatology", "Family Practice", "Interventional Pain Management",
    "Gastroenterology", "Internal Medicine", "Osteopathic Manipulative Medicine",
    "Neurology", "Neurosurgery", "Obstetrics/Gynecology", "Hospice/Palliative Care",
    "Ophthalmology", "Oral Surgery (Dentist Only)", "Orthopedic Surgery",
    "Cardiac Electrophysiology", "Pathology", "Sports Medicine",
    "Plastic And Reconstructive Surgery", "Physical Medicine And Rehabilitation",
    "Psychiatry", "Geriatric Psychiatry", "Colorectal Surgery (Proctology)",
    "Pulmonary Disease", "Diagnostic Radiology", "Thoracic Surgery",
    "Urology", "Chiropractic", "Nuclear Medicine", "Pediatric Medicine",
    "Geriatric Medicine", "Nephrology", "Hand Surgery", "Optometry",
    "Certified Nurse Midwife", "Certified Registered Nurse Anesthetist",
    "Infectious Disease", "Endocrinology", "Podiatry", "Nurse Practitioner",
    "Psychologist Billing Independently", "Rheumatology", "Clinical Psychologist",
    "Registered Dietitian Or Nutrition Professional", "Pain Management",
    "Peripheral Vascular Disease", "Vascular Surgery", "Cardiac Surgery",
    "Addiction Medicine", "Clinical Social Worker", "Critical Care (Intensivists)",
    "Hematology", "Hematology/Oncology", "Preventative Medicine",
    "Maxillofacial Surgery", "Neuropsychiatry", "Other (Non-Physician)",
    "Clinical Nurse Specialist", "Medical Oncology", "Surgical Oncology",
    "Radiation Oncology", "Emergency Medicine", "Interventional Radiology",
    "Physician Assistant", "Gynecological Oncology", "Other (Physician)",
    "Sleep Laboratory/Medicine", "Interventional Cardiology", "In-Person MDPP Supplier"
  ))

cd |>
  gt::gt() |> 
  gt::fmt_markdown(columns = Code) |> 
  gtExtras::gt_theme_nytimes() |> 
  gtExtras::gt_merge_stack(col1 = Type, 
                           col2 = Subtype,
                           small_cap = FALSE,
                           font_size = c("16px", "14px"),
                           font_weight = c("bold", "normal"),
                           palette = c("black", "darkgray")) |> 
  gt::opt_stylize(style = 4, color = "gray", add_row_striping = FALSE) |> 
  gt::opt_table_lines(extent = "default") |> 
  gt::opt_table_outline(style = "none")
```


### Related Links

 -   [Medicare Fee-For-Service Public Provider Enrollment API](https://data.cms.gov/provider-characteristics/medicare-provider-supplier-enrollment/medicare-fee-for-service-public-provider-enrollment)
 -   [Medicare Fee-For-Service Public Provider Enrollment - Data Dictionary](https://data.cms.gov/sites/default/files/2022-07/adb9dd34-73da-4488-855f-f091a648f87c/Medicare%20Fee-For-Service%20Public%20Provider%20Enrollment%20Data%20Dictionary.pdf)
 -   [Fee-For-Service Public Provider Enrollment Methodology](https://data.cms.gov/resources/fee-for-service-public-provider-enrollment-methodology)


<br><br>
