---
title: "Medicare Opt Out Affidavits API"
output: html_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

```{r}
library(provider)
```

<br>

> *A List of Practitioners Who are Currently Opted Out of Medicare.*

<br>

Physicians and practitioners who do not wish to enroll in the Medicare program may “opt-out” of Medicare. This means that neither the physician, nor the beneficiary submits the bill to Medicare for services rendered. Instead, the beneficiary pays the physician out-of-pocket and neither party is reimbursed by Medicare. A private contract is signed between the physician and the beneficiary that states that neither one can receive payment from Medicare for the services that were performed.

Opt-out periods last for two years and cannot be terminated early unless the provider is opting out for the very first time and he or she terminates their opt-out no later than 90 days after the effective date of their first opt-out period. Physicians and practitioners may NOT opt-out if they intend to be a Medicare Advantage (Part C) provider or furnish services covered by traditional Medicare fee-for-service (Part B).

Opt-out statuses are effective for two years. Opt-out affidavits signed on or after June 16, 2015 will automatically renew every two years. Physicians and practitioners that file valid opt-out affidavits effective on or after June 16, 2015 and do not want to extend their opt-out status at the end of a two year opt-out period may cancel by notifying all Medicare contractors with which they filed an affidavit in writing at least 30 days prior to the start of the next two year opt-out period.

The Opt Out Affidavits dataset provides information on providers who have decided not to participate in Medicare. It contains provider's NPI, specialty, address, and effective dates.

If you retire, surrender your license, or no longer want to participate in the Medicare program, you must officially withdraw within 90 days. DMEPOS suppliers must withdraw within 30 days.

What does it mean to opt out of Medicare?
You don’t want to bill Medicare for your services, but instead want your Medicare patients to pay out of pocket. Medicare coverage would apply when you order or certify items and services.

Please note, your decision to opt out will be made public on the CMS Opt-Out Dataset.

Impacts on Medicare Advantage (MA) plans:

May not pay (directly or indirectly) on any basis, for basic benefits furnished to a Medicare enrollee by a physician or other practitioner (as noted below) who has filed a valid opt-out affidavit with Medicare, and
Must pay for urgent care or emergency services furnished by a physician or practitioner who has not signed a private contract with the beneficiary they are treating.
May make payment to an opted-out physician or practitioner for services that are not basic benefits, but are provided to a beneficiary as a supplemental benefit consistent with regulations found at 42 CFR §422.102.
To opt out, you will need to:

Be of an eligible type or specialty.
Submit an opt-out affidavit to Medicare.
Enter into a private contract with each of your Medicare patients. This contract will reflect the agreement between you and your patients that they will pay out of pocket for services, and that nobody will submit the bill to Medicare for reimbursement.
Contact your Medicare Administrative Contractor (MAC) (PDF) to see what information you should include in your opt-out affidavit and private contract.

<br>

## Search Examples

```{r}
opt_out(last = "Aaron")
```
<br>

```{r}
opt_out(specialty = "Psychiatry", zip = "07626")
```
<br>

```{r}
opt_out(first = "David", last = "Smith")
```
<br>

```{r}
opt_out(npi = 1114974490)
```
<br>


```{r}
opt_out(city = "Los Angeles", address = "9201 W SUNSET BLVD")
```

<br>

### Data Dictionary

```{r echo=FALSE}
tibble::tibble(
  Variable = c(
    "`first_name`", "`last_name`", "`npi`", "`specialty`", "`optout_effective_date`",
    "`optout_end_date`", "`first_line_street_address`", "`second_line_street_address`",
    "`city_name`", "`state_code`", "`zip_code`", "`eligible_to_order_and_refer`"
  ),
  Description = c(
    "First Name", "Last Name", "NPI", "Specialty", "Optout Effective Date",
    "Optout End Date", "First Line Street Address", "Second Line Street Address",
    "City Name", "State Code", "Zip Code", "Eligible to Order and Refer"
  ),
  Definition = c(
    "First Name of the Opt Out Provider", "Last Name of the Opt Out Provider",
    "National Provider Identifier (NPI) number of the Opt Out Provider",
    "Specialty of the Opt Out Provider", "Date from which the Provider's Opt Out Status is effective",
    "Date on which the Provider's Opt Out Status ends", "Provider's Street Address",
    "Provider's Street Address", "Provider's City", "Provider's State Abbreviation",
    "Provider's Zip Code", "Flag indicating whether the Provider is eligible to Order and Refer")) |> 
  gt::gt() |> 
  gt::fmt_markdown(columns = Variable) |> 
  gtExtras::gt_theme_nytimes() |>
  gtExtras::gt_merge_stack(col1 = Description, 
                           col2 = Definition,
                           small_cap = FALSE,
                           font_size = c("16px", "14px"),
                           font_weight = c("bold", "normal"),
                           palette = c("black", "darkgray")) |> 
  gt::opt_stylize(style = 4, color = "gray", add_row_striping = FALSE) |> 
  gt::opt_table_lines(extent = "default") |> 
  gt::opt_table_outline(style = "none")
```

<br>

### Related Links

   - [Medicare Opt Out Affidavits API](https://data.cms.gov/provider-characteristics/medicare-provider-supplier-enrollment/opt-out-affidavits)

<br><br>

