---
title: "NPPES NPI Registry API"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

```{r}
library(provider)
```

> insert quick summary

## Purpose

The [NPPES NPI Registry Public Search](https://npiregistry.cms.hhs.gov/) is a free directory of all active **National Provider Identifier** (NPI) records. Healthcare providers acquire their unique 10-digit NPIs to identify themselves in a standard way throughout their industry. After CMS supplies an NPI, they publish the parts of the NPI record that have public relevance, including the provider's name, specialty (taxonomy) and practice address. It enables you to search for providers in the NPPES (National Plan and Provider Enumeration System.) All information produced by the NPI Registry is provided in accordance with the NPPES Data Dissemination Notice. There is no charge to use the NPI Registry.

The NPPES *Application Programming Interface* (API) is a faster alternative to the [downloadable NPPES data files](https://www.cms.gov/Regulations-and-Guidance/Administrative-Simplification/NationalProvIdentStand/DataDissemination.html). It allows systems to access NPPES public data in real-time, rather than through batched uploads. The API retrieves data from NPPES daily. An API query will return a maximum of 200 results per request. The *Skip* field in the API will let you skip up to 1000 records. By using these two fields with your search criteria, you can get up to a maximum of 1,200 records over six requests.

<br>

## Examples

```{r message=FALSE, warning=FALSE}
nppes_npi(1114499340)
```


<br><br>

This returns a `tibble` containing the NPI that was searched for (`search`), the `datetime` of the query, an `outcome` status column and `data_lists`, a list-column containing a collection of variables and nested data frames:

<br>

The **variables** returned are as follows:

<br>

 * `created_epoch`: date when the NPI was issued
 * `enumeration_type`: NPI Entity Type, either NPI-1(individual) or NPI-2(organizational)
 * `last_updated_epoch`: date when the information was last updated by the provider
 * `number`: provider's NPI, as listed in the NPPES

<br>

> Note: `last_updated_epoch` / `created_epoch` are dates in [Unix time](https://www.epochconverter.com/). They are repeated in the `basic` list as `last_updated` and `enumeration_date`, respectively.

<br>

The **list-columns** returned are as follows:

<br>

 * `basic`: Basic information
 * `other_names`: Other names used by the provider
 * `addresses`: Primary location and mailing addresses
 * `taxonomies`: Specialty classification and related information
 * `identifiers`: Various other identifiers such as payer-specific IDs, CLIA numbers, etc.
 * `practice_locations`: Provider's practice locations
 * `endpoints`: Information regarding the provider's endpoints for Health Information Exchange (HIE)

<br><br>
 
> Note: All list-columns may not be available for every provider. This depends on factors such as NPI type, incorporated individual status, subpart delegation, and, quite simply, the information provided to the NPPES by providers.

<br>


# API Documentation Overview

<br>

This section outlines the NPPES API's documentation, going over valid search inputs, constraints to those inputs, and descriptions of the many possible outputs.

<br>

## Terminology Notes

<br>

### Enumeration Type

<br>
Two categories of health care providers exist for NPI enumeration purposes: Entity *Type 1* (Individual) and Entity *Type 2* (Organizational).
<br>

#### NPI-1: Individual

Individual health care providers (including sole proprietors) may get an NPI as **Entity Type 1**. As a sole proprietor, they must apply for the NPI using your own SSN, not an Employer Identification Number (EIN) even if they have an EIN. As a sole proprietor, they may get only one NPI, just like any other individual.

The following factors **do not** affect whether a sole proprietor is an Entity Type 1:

-   Number of different office locations
-   Whether they have employees
-   Whether the IRS issued them an EIN.


> An **incorporated individual** is a single health care provider who forms and conducts business under a corporation. A sole proprietor **is not** an incorporated individual because the sole proprietor didn't form a corporation. If you're a sole/solo practitioner, it doesn't necessarily mean you're a sole proprietor, and vice versa. If you're an individual health care provider who's incorporated, you may need to get an NPI for yourself (Entity Type 1) and an NPI for your corporation or LLC (Entity Type 2).

<br>

#### NPI-2: Organizational

<br>

Organizational health care providers are group health care providers eligible for NPIs as Entity Type 2. Organization health care providers may have a single employee or thousands of employees. An example is an incorporated individual who is an organization's only employee.

Some organization health care providers are made up of parts that work somewhat independently from their parent organization. These parts may offer different types of health care or offer health care in separate physical locations. These parts and their physical locations aren't themselves legal entities but are part of the organization health care provider (which is a legal entity). The NPI Final Rule refers to the parts and locations as subparts.

An organization health care provider can get its subparts their own NPIs. If a subpart conducts any HIPAA standard transactions on its own (separately from its parent), it must get its own NPI. Subpart determination makes sure that entities within a covered organization are uniquely identified in HIPAA standard transactions they conduct with Medicare and other covered entities. For example, a hospital offers acute care, laboratory, pharmacy, and rehabilitation services. Each of these subparts may need its own NPI because each sends its own standard transactions to one or more health plans.

> Subpart delegation doesn't affect Entity Type 1 health care providers. As individuals, these health care providers can't choose subparts and are not subparts.

<br>

#### Authorized Official

<br>

An appointed official (e.g., chief executive officer, chief financial officer, general partner, chairman of the board, or direct owner) to whom the organization has granted the legal authority to enroll it in the Medicare program, to make changes or updates to the organization's status in the Medicare program, and to commit the organization to fully abide by the statutes, regulations, and program instructions of the Medicare program. See 42 CFR 424.502 for additional information.

<br><br>

