---
title: "Quality Payment Program"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

```{r}
library(provider)
```

<br>

> The **Quality Payment Program (QPP) Experience** dataset provides participation and performance information in the Merit-based Incentive Payment System (MIPS) during each performance year. They cover eligibility and participation, performance categories, and final score and payment adjustments. The dataset provides additional details at the TIN/NPI level on what was published in the previous performance year. You can sort the data by variables like clinician type, practice size, scores, and payment adjustments.

<br>

## Examples

```{r}
quality_payment(year = 2018, npi = 1578508776)
```

<br><br>


```{r}
quality_eligibility(year = 2018, npi = 1578508776, tidy = FALSE)
```
<br><br>

```{r}
quality_stats(year = 2018)
```

<br><br>
