---
title: "Quality Payment Program"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE, 
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

```{r}
library(provider)
```

<br>

> The **Quality Payment Program (QPP) Experience** dataset provides participation and performance information in the Merit-based Incentive Payment System (MIPS) during each performance year. They cover eligibility and participation, performance categories, and final score and payment adjustments. The dataset provides additional details at the TIN/NPI level on what was published in the previous performance year. You can sort the data by variables like clinician type, practice size, scores, and payment adjustments.

<br>


```{r}
qpp_ga <- 2017:2021 |> 
  furrr::future_map(\(x) quality_payment(year = x, 
                                         state = "GA", 
                                         specialty = "Internal Medicine", 
                                         part_type = "Individual")) |> 
  purrr::list_rbind()
```


```{r}
qpp_ga |> 
  dplyr::group_by(year) |> 
  dplyr::summarise(n = dplyr::n(),
                   avg_yrs = mean(med_yrs, na.rm = TRUE),
                   med_size = median(practice_size, na.rm = TRUE),
                   avg_size = mean(practice_size, na.rm = TRUE),
                   avg_benes = mean(beneficiaries, na.rm = TRUE),
                   avg_services = mean(services, na.rm = TRUE),
                   avg_charges = mean(allowed_charges, na.rm = TRUE),
                   avg_score = mean(final_score, na.rm = TRUE), 
                   avg_pmt_adj = mean(pmt_adj_pct, na.rm = TRUE),
                   n_opted_into_mips = sum(opted_into_mips, na.rm = TRUE),
                   .groups = "drop")
```

